---
title: "tech meetup"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=F, warning=F)
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(RColorBrewer)
library(plotly) #contain hex to RGB conversion
library(data.table)
library(viridis)
library(ggrepel)
#date
library(lubridate)
#machinelearning
library(caret)
#json
library(jsonlite)
#text
library(tidytext)
library(wordcloud2)
#theme
my_theme <- function(base_size = 10, base_family = "Helvetica"){
    theme_minimal() +
    theme(
    plot.title = element_text(face="bold", size=16),
    axis.text = element_text(face="bold"),
    plot.background = element_rect(fill = 'ghostwhite',color='white'),
    legend.position = 'None', legend.title = element_blank())
}

```

Using Singapore tech meetup data curated by webuild.sg, we seek to answer the following questions:

* how do the meetup groups compare to each other
* what's the RSVP distribution by meetup group/hour/topic/title/location/platform/title of speakers/target audience
* infer how to run a successful meetup

## Load data

We will use past 1 year of data from Oct 2016 to 2017 based on recency and relevancy

```{r input}
#data source: https://github.com/webuildsg/data/tree/gh-pages/data/events/v1
#setwd("/Users/hannah/git_repo/opendata_viz/tech_meetup_sg")
df=fromJSON("Data/events_archive_2016_10_01_030109.json") %>% as.data.frame()
```

```{r jsonlist}
#loop through files
files <- list.files(path="data", pattern="*.json", full.names=T, recursive=FALSE)

```

The json file partitioned by day could contain anything from 0 to multiple events. 

To handle the multiple csv row per iteration, we can use rbindlist from data.table package. 

We also need to use tryCatch to handle json files with 0 event on that day.

```{r}
mylist <- list() #create an empty list

for (i in 1:370) {
  mylist[[i]] <- tryCatch(fromJSON(files[i]) %>% as.data.frame(),
                          error=function(e){return(NA %>% as.data.frame())})
}
df <-rbindlist(mylist, fill=TRUE) 

#make colnames shorter
names(df) <- gsub('^events.?','',names(df))
df <- df %>% filter(!is.na(meta.total_events)) %>%
  mutate(start_time = ymd_hms(start_time),
         end_time = ymd_hms(end_time),
         hour = hour(start_time),
         wday = wday(start_time))

write.csv(df,'tech_meetup_sg.csv', row.names = FALSE)
```

```{r}
df_group <- df %>% count(group_name, sort=T) %>% filter(n>=6)
```



## EDA
focus on the groups with more than 6 events last year. Among them most groups fall into 6-10 events and 50-100 RSVPs.
```{r}
df_smry <- df %>%
  group_by(group_name) %>%
  summarize(num_events=n(), median_rsvp = median(rsvp_count)) %>%
  mutate(num_events_bkt = cut_interval(num_events, length=10),
         median_rsvp_bkt = cut_interval(median_rsvp, length=50))

df_smry_bkt <- df_smry %>%
  inner_join(df_group, by = "group_name") %>%
  group_by(num_events_bkt, median_rsvp_bkt) %>%
  count(n = n())

sample<- df_smry %>% filter(num_events<10,num_events>6, median_rsvp<=25)
df_smry %>%
  inner_join(df_group, by = "group_name") %>%
  ggplot(aes(num_events, median_rsvp, col=median_rsvp))+
  geom_point() + 
  geom_text(aes(label=ifelse(num_events>=30|median_rsvp>=100, group_name,"")),size=3,  hjust=-0.03) +
  scale_colour_gradient(low = "skyblue",high = "purple")+
  my_theme() + 
  labs(title = 'Tech Meetups in Singapore', subtitle = 'Number of events hosted and median RSVP on Meetup, Facebook or Eventbrite during 2016 Oct - 2017 Oct') 
```


Now let's zoom out to 173 tech meetup groups with RSVP only. Sadly most meetup groups didn't sustain - they had <5 events with <25 rsvps.

```{r heatmap}
df_smry %>% na.omit()  %>%
  count(num_events_bkt, median_rsvp_bkt) %>%
  ggplot(aes(num_events_bkt, median_rsvp_bkt)) + geom_tile(aes(fill=n)) + 
  scale_fill_gradient(low = "#ffe1e1",high = "#ffb7b7") + 
  my_theme()
```

How do different factors affect RSVP
```{r}
df_features <- df(hour, wday, platform, )
```

Frequent words in titles

```{r}
df %>% 
  filter(!is.na(name)) %>%
  select(name) %>%
  unnest_tokens(word, name) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```
#sentence cloud??
keys word and their associated words

Extract topic after 'intro(duction) to' and before:/-/workshop
Introduction to ...?
```{r}
df_intro <- df %>% 
  select(name) %>%
  filter(grepl("Intro", name)) %>%
  mutate(topic = gsub(".*Intro.* to","", name)) %>%
  mutate(topic = gsub(" Workshop","", topic))  %>%
  mutate(topic = gsub(" -.*","", topic)) %>%
  mutate(topic = gsub(":.*","", topic)) %>%
  mutate(topic = gsub("\\(PAID\\)","", topic)) %>%
  mutate(topic = gsub("Through Pairs Trading","", topic))%>%
  mutate(topic = gsub("Introduction","", topic)) %>%
  mutate(topic = trimws(topic))

```

```{r}
topic <- df_intro %>% count(topic) %>%  mutate(n=1)
  #only very few are 2 which isn't particularly meaningful to show size 
wordcloud2(topic, size = 0.08, minRotation = -pi/12, maxRotation = pi/12,
  rotateRatio = 1)

```
topic)
```

#to-do: location: need to bin coordinates in East/W/N/S/Central

## Modeling

So how to run a successful meeting? In my hypothesis, the RSVPs are related with:

1. user base (how many people have signed up for the group, a.k.a how good the marketing is). However this requires an additional scrap of 3 websites on membership counts so we will leave it for now.
2. convenience of the event (central location, good timing after work)
3. value of the event (i.e. catchy topic, hot technology, prestigious speaker)
4. others (i.e. free pizza and beer)

There would be other factors affecting the actual turnout (i.e. weather of the day) which isn't our focus here.


So meanwhile we can use features like timing, weekday, location, channel (fb/meetup/eventbrite), keywords (i.e. contain 'introduction', or 'data science')


## Takeaways