---
title: "cherry_blossom"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=F, warning=F)
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(RColorBrewer)
library(plotly) #contain hex to RGB conversion
#date
library(lubridate)
#theme
my_theme <- function(base_size = 12, base_family = "Helvetica"){
    theme_minimal() +
    theme(axis.title.y = element_blank(),axis.title.x = element_blank(),
    plot.title = element_text(face="bold", size=16),
    axis.text = element_text(face="bold"),
    plot.background = element_rect(fill = 'ghostwhite',color='white'),
    legend.position = 'None', legend.title = element_blank())
}

```

## Load data
```{r}
cherry_blossom <- read.csv("~/git_repo/opendata_viz/cherry_blossom/cherry_blossom.csv") %>%
  mutate(flowering.dt=ymd(paste0('2018 ',Flowering.date)),
         fullbloom.dt=ymd(paste0('2018 ',Full.bloom.date)))
df <- cherry_blossom %>%
  filter(!is.na(Region))  %>%
  select(Region, Prefecture, Location, Flowering.date, Full.bloom.date) %>%
  gather(key, value, -Region, -Prefecture, -Location) %>%
  mutate(dt = ymd(paste0('2018 ',value)),
         Location = as.character(Location)) 
```

# simulate flowering cycle
it takes about 1 wk to reach full blossom which lasts about another wk, according to Japan-info

add a simulated delay days mirroring flowering-to-full bloom duration
```{r}
#fill up the date for interpolate color gradient
df_dummy <- df %>%
  group_by(Prefecture, Region, Location) %>%
  complete(dt = seq.Date(min(dt), max(dt), by="day")) %>%
  mutate(idx = 1:n())

df_dummy2 <- df_dummy %>%
  complete(dt = seq.Date(max(dt), max(dt) + (max(dt) - min(dt)), by="day")) %>%
  arrange(desc(dt)) %>%
  mutate(idx = 1:n())

df_cycle <- df_dummy %>%
  rbind(df_dummy2) %>%
  unique()

# now fill those with no value too
df_filled <- df_cycle %>%
  group_by(Prefecture, Region, Location) %>%
  complete(dt = seq.Date(min(df$dt), max(df$dt), by="day"))
df_filled$idx[is.na(df_filled$idx)] <- 0
write.csv(df_filled, 'df_cherryblossom.csv')
```

#make a palette of 13 color from viridis magma
```{r}
pal <- colorRampPalette(c("#FFF7F3", "#DD3497"))
paste0("<color>",pal(14),"</color>")
```

## the number of cities where cherry blossom is between flowering to full bloom stage
```{r}
df_count <- df_dummy %>%
  group_by(dt) %>%
  summarize(n = n_distinct(Prefecture)) %>%
  complete(dt = seq.Date(min(dt), max(dt), by="day"))
df_count$n[is.na(df_count$n)] <- 0
write.csv(df_count, 'df_count.csv')
```

process cherry-blossom-viewable locations by the same dt as well


## control gantt chart
```{r fun}
viewable <- function(dt) {
  df_temp <- cherry_blossom %>%
    filter(flowering.dt<=dt, fullbloom.dt>=dt)
  return(df_temp)
}
```

```{r}
dt_seq <- seq.Date(min(df$dt), max(df$dt), by="day")
all_viewable <- dt_seq %>%
  map_dfr(viewable) 

all_viewable_dt <- all_viewable %>%
  group_by(Location) %>%
  mutate(idx = 1:n()) %>%
  mutate(dt = first(flowering.dt) + idx - 1)
write.csv(all_viewable_dt, 'all_viewable_dt.csv')
```

