
```{r}
Salaries <- read.csv("~/Python/Salaries.csv", stringsAsFactors=FALSE, na=c("Not Provided"))

library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape2)
library(formattable)
```{r}
#cleaning data
Salaries%>%
  mutate(BasePay=as.numeric(BasePay))%>%
  mutate(OvertimePay=as.numeric(OvertimePay))%>%
  mutate(OtherPay=as.numeric(OtherPay))%>%
  mutate(Benefits=as.numeric(Benefits))
Salaries=Salaries[Salaries$TotalPayBenefits>=0,]
#salaries over the years
Salaries%>%ggplot(aes(x = TotalPayBenefits)) +
     geom_boxplot(aes(fill = factor(Year)), alpha = 0.6)

#income disparity by pay type across the years
Salaries%>%
  select(Year,JobTitle,BasePay,OvertimePay, OtherPay,Benefits,
         TotalPayBenefits )%>%
  melt(id=c("JobTitle","Year"))%>%
  ggplot(aes(x=variable,y=value))+geom_boxplot(aes(fill=variable))+facet_wrap(~Year)+ggtitle('Income Variation by Type 2011-2014')

#distribution of pay types
```

```{r}
#how do totalpaybenefits changes over the year
Salaries%>%
  select(Year,TotalPayBenefits)%>%
  ggplot(aes(factor(Year),TotalPayBenefits))+geom_violin(aes(fill=factor(Year)))+ggtitle('Total Pay Over the Years')
```
```{r}

#top-paid FT job
Salaries%>%
  filter(Year==2014&Status=='FT')%>%
  arrange(desc(TotalPayBenefits))%>%
  head(10)%>%
  mutate(TotalPayBenefits=round(TotalPayBenefits,0))%>%
  select(JobTitle,TotalPayBenefits)%>%
   formattable(list(TotalPayBenefits = color_bar("lightblue",0.9)),
    align = 'l')
#bottom-paid FT job
Salaries%>%
  filter(Year==2014&TotalPayBenefits>0&Status=='FT')%>%
  arrange(desc(TotalPayBenefits))%>%
  select(JobTitle,TotalPayBenefits)%>%
  mutate(TotalPayBenefits=round(TotalPayBenefits,0))%>%
    tail(10)%>%
   formattable(list(TotalPayBenefits = color_bar("pink",0.9)),
    align = 'l')

Q25%>%
  arrange(desc(TotalPayBenefits))%>%
  head()%>%
  select(JobTitle,TotalPayBenefits)%>%
   formattable(
    list(TotalPayBenefits = color_bar("pink",1)),
    align = 'l') 

#what jobs return highest quartile of salaries
Q75=Salaries%>%
  filter(TotalPayBenefits>=quantile(TotalPayBenefits,0.75))
library(tm)
library(SnowballC)
library(wordcloud)
jobcorpus <- Corpus(VectorSource(Q75$JobTitle))
jobcorpus <- tm_map(jobcorpus, PlainTextDocument)
jobcorpus <- tm_map(jobcorpus, removePunctuation)
jobcorpus <- tm_map(jobcorpus, removeWords, stopwords('english'))
wordcloud(jobcorpus, max.words = 100, random.order = FALSE,colors=brewer.pal(8, 'Dark2'))
```

```{r}
#what jobs return lowest quartile of salaries
Q25=Salaries%>%
  filter(TotalPayBenefits<=quantile(TotalPayBenefits,0.25))
jobcorpus <- Corpus(VectorSource(Q25$JobTitle))
jobcorpus <- tm_map(jobcorpus, PlainTextDocument)
jobcorpus <- tm_map(jobcorpus, removePunctuation)
jobcorpus <- tm_map(jobcorpus, removeWords, stopwords('english'))
wordcloud(jobcorpus, max.words = 100, random.order = FALSE,colors=brewer.pal(8, 'Dark2'))
```
```{r}
sfm=Salaries%>%
  select(BasePay,OvertimePay,OtherPay)
sfscaled=as.matrix(scale(sfm))
```

