---
title: ""
output: 
    html_document: 
      toc: true
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
# This is a code block
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(caret) # Data visualization
library(viridis)
library(RColorBrewer)
library(lubridate)
library(ggbeeswarm)
#visualization
library(formattable)
library(tweenr)
library(gganimate)
library(dplyr)
library(ggjoy)
#text
library(Hmisc)
library(spacyr)
#modeling
library(rpart)
library(rpart.plot)
library(arules)
library(arulesViz)
spacy_initialize(python_executable = "/Users/hannah/anaconda/bin/python")
#theme
my_theme <- function(base_size = 12, base_family = "Helvetica"){
    theme_minimal() +
    theme(axis.title.y = element_blank(),axis.title.x = element_blank(),
    plot.title = element_text(face="bold", size=16),
    axis.text = element_text(face="bold"),
    plot.background = element_rect(fill = 'ghostwhite',color='white'),
    legend.position = 'None', legend.title = element_blank())
}

```

```{r input, message=FALSE}
start_eda=Sys.time()
#data https://www.kaggle.com/hugodarwood/epirecipes
epicurious_recipes_original <- read_csv("~/git_repo/opendata_viz/epicurious_recipes/epicurious_recipes.csv")

```

Each recipe have multiple tags conveying a plurality of information:

* state name: Alabama
* drink name: bon apetit
* meal type: breakfast
* festival: 4th of jul
* season: summer
* diet type: soy free
* cooking method: braise
* ingredient: beef. 

We need to parse out these different entities

##proprocessing
Remove outliers
```{r preprocess}
epicurious_recipes <- epicurious_recipes_original %>%
  mutate(rating_rounded = round(rating)) %>%
  mutate(rating_bkt = ifelse(rating_rounded>=4,"good",
                             ifelse(rating_rounded==3,"ok","bad"))) %>%
  filter(fat<quantile(fat,.8, na.rm=T), 
         calories<quantile(calories, .8, na.rm=T), 
         protein<quantile(protein,.8, na.rm=T),
         sodium<quantile(sodium,.8, na.rm=T))
```

##rating vs nutrients
```{r}
content <- epicurious_recipes %>%
  select(c(calories:sodium, rating_bkt))%>%
  na.omit() %>%
  gather(key, value, -rating_bkt)

content$rating_bkt <- factor(content$rating_bkt, levels = c("bad", "ok", "good"))
```

```{r fun1_plot}
plot_density = function (df, facet) {
  ggplot(df, aes(x=value,y=facet, fill=facet, alpha=0.6)) + 
  geom_joy() + facet_wrap(~key, scales="free", nrow=2) +
  labs(title='recipe rating vs nutrients', caption='source: Epicurious')+
  my_theme()+guides(alpha=FALSE) 
}
```

```{r}
plot_density(content, content$rating_bkt)
```


##most common ingredient
```{r mostcommoningredient}
tag <- epicurious_recipes %>% 
  select(alabama:turkey) %>%
  summarise_all(sum) %>%
  gather(tag, count) %>%
  arrange(desc(count)) %>%
  mutate(tag = capitalize(tag))
```

```{r}
parsedtxt <- spacy_parse(tag$tag)
```

```{r fun2_bar}
tabularize = function(i) {
  i %>%
    select(-c(rating, calories:sodium)) %>%
    summarize_all(sum) %>% 
    gather(category,count) %>%
    arrange(desc(count)) %>%
    formattable(list(count = color_bar("pink")),
    align = 'l')}
```

```{r fun3_transpose_columns}
transpose_columns = function (x) {
df_total = x %>% 
  mutate(total = rowSums(select(., -c(rating:sodium))))%>%
  filter(total==1)

df_lean = df_total %>%select(-c(rating:total))

whichfield=function(x) colnames(df_lean)[[which(x==1)]]
df_lean$field=apply(df_lean,1,whichfield)

df_transposed=df_total%>%
  select(-c(1:4)) %>%
  bind_cols(df_lean) %>%
  select(c(calories:sodium, field)) %>%
  gather(key, value, -field)
return(df_transposed)
}
```

```{r fun4_select}
df_select = function(x) {
  epicurious_recipes %>% 
  select(c(one_of(x),rating, calories:sodium)) %>%
  select(-one_of('turkey','saffron','rye','chartreuse'))%>%
  na.omit()
}
```



##rating vs state
```{r}
state <- parsedtxt %>% filter(entity == 'GPE_B')

df_state <- df_select(state$lemma)

df_state%>%select(-rating)%>%summarize_all(sum)

tabularize(df_state)
```


```{r fig.length=12}
plot_density(transpose_columns(df_state),  transpose_columns(df_state)$field)
```


##meal vs nutrients
```{r}
meal = c('breakfast','brunch','lunch','dinner')

df_meal <- df_select(meal)

df_meal %>% select(-rating) %>% summarize_all(sum)
tabularize(df_meal)
```




```{r}
df_meal_nutrient <- transpose_columns(df_meal) 

#reorder factor
df_meal_nutrient$field <- factor(df_meal_nutrient$field, 
                                 levels = c("dinner", "lunch", "brunch","breakfast"))
#plot rating vs nutrients
plot_density(df_meal_nutrient, df_meal_nutrient$field) +
  labs(title='meal vs calories, fat, protein and sodium', caption='source: Epicurious')
```


##season vs nutrients
```{r}
#filter for meal tagged to one season only
season = c('spring','summer','fall','winter')

df_season<- df_select(season)

df_season%>%select(-rating)%>%summarize_all(sum)
tabularize(df_season)
```
```{r}
df_season_nutrient <- transpose_columns(df_season) 

df_season_nutrient$field <- factor(df_season_nutrient$field, 
                                 levels = c("winter", "fall", "summer","spring"))
#plot rating vs nutrients

plot_density(df_season_nutrient, df_season_nutrient$field) +
  labs(title='seasonal meal vs calories, fat, protein and sodium', caption='source: Epicurious')
```


##holiday vs nutrients
```{r}
holiday = c('christmas','fourth of july','passover','thanksgiving','easter','new year\'s eve')

df_holiday<- df_select(holiday)

tabularize(df_holiday)
```

```{r}
df_holiday_nutrient <- transpose_columns(df_holiday) 

plot_density(df_holiday_nutrient, df_holiday_nutrient$field) +
  labs(title='holiday meal vs calories, fat, protein and sodium', caption='source: Epicurious')
```
##technique vs nutrients
```{r}
technique <- c('grill/barbecue','bake','roast','braise','fry','stir-fry','pan-fry','saute','no-cook')
df_technique <- df_select(technique)
tabularize(df_technique)
```
```{r}
df_technique_nutrient <- transpose_columns(df_technique) 

plot_density(df_technique_nutrient, df_technique_nutrient$field) +
  labs(title='technique vs nutrients', caption='source: Epicurious')
```

#diet vs nutrients
```{r}
diet <- c('vegetarian','kosher',
               'gourmet','kidney friendly', 'vegan','healthy','Low cholesterol','wheat/gluten-free')

other_diet <- c('soy free', 'peanut free','bon appétit','pescatarian','tree nut free','dairy free','no sugar added','kosher for passover')
df_diet <- df_select(diet)
tabularize(df_diet)
```

```{r}
df_diet_nutrient <- transpose_columns(df_diet) 

plot_density(df_diet_nutrient, df_diet_nutrient$field) + 
  labs(title='diets vs nutrients', caption='source: Epicurious')
```


##ingredients

```{r}
drinks=c('drink','drinks','cocktail party')
df_ingredient <- epicurious_recipes %>% 
  select(-c(1:6))%>% 
  select(-one_of(meal,  diet,
                               other_diet, drinks)) %>%
  na.omit()
```


```{r}
data = df_ingredient%>%
       mutate_all(funs(factor(.)))
```



## association rules
Which ingredients appear together?
Which non-ingredient tag are associated with good or bad?

```{r fun5_arule}
idx <- which(data==1, arr.ind = T)
lst <- split(names(data)[idx[,2]], idx[,1])
rules <- function(x, supp, rhs) { 
  x %>% 
    as("transactions") %>% 
    apriori(parameter=list(minlen=2, maxlen=4, supp=supp,conf = 0.5), 
            appearance = list(default="lhs",rhs=rhs),
            control = list(verbose=F)) 
}
```
```{r}
rules_all <- function(x, supp) { 
  x %>% 
    as("transactions") %>% 
    apriori(parameter=list(minlen=2, maxlen=4, supp=supp,conf = 0.4), 
            #appearance = list(default="lhs",rhs=rhs),
            control = list(verbose=F)) 
}
```

```{r arule_holiday}
all.rules.sorted <- sort(rules_all(lst,0.001), by="lift")
all.rules.subset = subset(all.rules.sorted, subset = rhs %in% holiday
    & lift > 2)
plot(head(all.rules.subset,200), method="grouped")
```

```{r arule_season}
all.rules.sorted <- sort(rules_all(lst,0.002), by="lift")
all.rules.subset = subset(all.rules.sorted, subset = rhs %in% season
    & lift > 1)
plot(head(all.rules.subset,200), method="grouped")
```

```{r arule_state}
all.rules.sorted <- sort(rules_all(lst,0.001), by="lift")
all.rules.subset = subset(all.rules.sorted, subset = rhs %in% state$lemma
    & lift > 1)
plot(head(all.rules.subset,200), method="grouped")
```

```{r arule}
rules.sorted <- sort(rules(lst,0.001,"summer"), by="lift")
#inspect(head(rules.sorted,20))
plot(head(rules.sorted,60), method="graph",
     control = list(nodeCol = grey.colors(10), edgeCol = grey(.7), alpha = 0.9))
```



```{r}

```


