---
title: "ISIS Twitter Network"
output: 
    html_document: 
      toc: true
---

This article explores how ISIS followers spread information via Twitter Network, their primary social outlet
```{r message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(dplyr)
library(reshape2)
library(tidyr)
library(formattable)
library(RColorBrewer)
library(lubridate)
library(networkD3)
library(stringr)
library(visNetwork)
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
data <- read_csv("tweets.csv")
```

```{r warning=FALSE, echo=FALSE}
glimpse(data)
data=data%>%
mutate(time=mdy_hm(time))%>%
mutate(hour=hour(time))%>%
mutate(wday=wday(time, label = TRUE))%>%
mutate(month=month(time))%>%
mutate(year=year(time))%>%
arrange(time)%>%
mutate(yr_month=paste(year(time),month(time),sep='-'))%>%
mutate(date=ymd(paste(year(time),month(time),day(time),sep='-')))%>%
mutate(is_retweet = ifelse(grepl("^\\bRT\\b", tweets), "Retweets", "Originaltweets"))
```
#Followers
To understand the fanbase, let's look at their number of tweets vs number of followers
```{r message=FALSE, warning=FALSE, echo=FALSE}
fanbase=data%>%
select(name,followers,tweets)%>%
group_by(name)%>%
summarize(n_follower=max(followers),n_tweet=n())

wss <- numeric(15)
for (k in 1:15) {wss[k] <- sum(kmeans(as.matrix(fanbase[, 2:3]), centers=k,nstart=25)$withinss)}


set.seed(20)
ISIScluster <- kmeans(as.matrix(fanbase[, 2:3]), 4, nstart = 20)

fanbase%>%
ggplot(aes(n_tweet,n_follower))+
geom_point(aes(color=factor(ISIScluster$cluster)))+
geom_text(aes(label=ifelse(n_follower>7000|n_tweet>700,as.character(name),'')),vjust=1.5)+
guides(color=FALSE)+
ggtitle('Number of Tweets vs Followers') +
theme_classic()
```

Rami stands out with large number of follower and tweet activity.  
War Breaking News, Conflict Reporter and Salahuddin Ayubi has the most tweets activity

#Timeline of tweets

##activity types
```{r}
data%>%group_by(is_retweet)%>%
summarize(n_tweet=n())%>%
head()
```
It appears retweet vol is about half of original tweets.

##tweet/retweet activity by most active users
```{r}
data%>%
filter(name%in%c("Rami","War BreakingNews","Conflict Reporter","Salahuddin Ayubi"))%>%
select(date,tweets,is_retweet)%>%
arrange(date)%>%
group_by(date,is_retweet)%>%
summarize(n_tweet=n())%>%
ggplot(aes(date,n_tweet,fill=is_retweet))+
geom_bar(stat='identity',position='stack',color='white') +
theme_classic()
```
Activity peaked at:  
* Mar 17 (when news of ISIS killing Syrian poet broke out)
* Apr 05 (ISIS launched chemical weapon to attack Syrian army base)  
It appears all of these only started to be active since 2016 Feb


##hastags
Let's next look into hashtag applied everyday  

```{r hashtag}
hash=data%>%
  mutate(hash=str_extract_all(tweets, "#\\w+"))%>%
  select(hash)%>%
  filter(!is.na(hash))%>%
  unnest(hash)%>%
  group_by(hash)%>%
  summarize(n_hash=n())%>%
  arrange(desc(n_hash))
```
Could hashtag shed some light on what happened on the days of peak twitter activity?
```{r}
calloutdays=c('2016-03-11','2016-03-27','2016-04-05')
hashspecial=data%>%
  filter(date%in%calloutdays)%>%
  mutate(hash=str_extract(tweets, "#\\w+"))%>%
  select(date,hash)
```

##mentions
Let's also top handles mentioned  

```{r mention}
mention=data%>%
  mutate(mention=str_extract_all(tweets, "@\\w+"))%>%
  select(mention)%>%
  filter(!is.na(mention))%>%
  unnest(mention)%>%
  group_by(mention)%>%
  summarize(n_mention=n())%>%
  arrange(desc(n_mention))
mention%>%
  head(10)
```

#Mention Network
Due to sparse twitter activity in 2015, we zoom in to 2016
```{r warning=FALSE, fig.height=5,fig.width=10}
user=data%>%select(username)%>%unique()
links=data %>%
  select(from = username, tweets)%>%
  mutate(to = str_extract_all(tweets, '(?<=@)\\w+')) %>%
  filter(to != 'character(0)') %>%
  select(-tweets) %>%
  unnest(to) %>%
  mutate(flag = to %in% user$username) %>%
  filter(flag == TRUE) %>%
  filter(from != to) %>%
  select(-flag) %>%
  group_by(from,to) %>% 
  tally()

nodes=data.frame(id=unique( union(unique(links$from), unique(links$to))))
nodes=data%>%mutate(id=username)%>%
  group_by(id)%>%tally()
nodes$size <- sqrt(nodes$n)
nodes$title <-nodes$id
links$arrows <-'to'
links$width<- (links$n)^(1/3)
visNetwork(nodes, links, main='Twitter Network')%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) 
```
