---
title: "University ranking"
output: html_document
---
```{r, warning = FALSE, error = FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(ggthemes)
library(reshape2)
```


#Data 
```{r, warning = FALSE, error = FALSE, message=FALSE}

cwurData <- read.csv("~/R/Kaggle_Dataset/world-university-ranking/cwurData.csv", stringsAsFactors=FALSE)
school_and_country_table <- read.csv("~/R/Kaggle_Dataset/world-university-ranking/school_and_country_table.csv", stringsAsFactors=FALSE)
shanghaiData <- read.csv("~/R/Kaggle_Dataset/world-university-ranking/shanghaiData.csv", stringsAsFactors=FALSE)
timesData <- read.csv("~/R/Kaggle_Dataset/world-university-ranking/timesData.csv", stringsAsFactors=FALSE)

```

Each of the Ranking data contains ranking across years

```{r echo=FALSE, message=FALSE}
table(cwurData$year)
table(timesData$year)
table(shanghaiData$year)
```

2012-2015 are the common years
```{r}
yr=2015
```


#Variance between universities
```{r, warning = FALSE, error = FALSE, message=FALSE}
RankDiff=cwurData%>%
  filter(year==yr)%>%
  select(institution,cwur_rank=world_rank)%>%
  mutate(shanghai_rank=as.numeric(subset(shanghaiData,year==yr)$world_rank[match(institution,shanghaiData$university_name)]))%>%
  mutate(times_rank=as.numeric(subset(timesData,year==yr)$world_rank[match(institution,timesData$university_name)]))%>%
  mutate(country=school_and_country_table$country[match(institution,school_and_country_table$school_name)])%>%
  rowwise()%>%
  mutate(lowest_rank=(pmax(cwur_rank,times_rank,shanghai_rank)),
    highest_rank=(pmin(cwur_rank,times_rank,shanghai_rank)))%>%
  filter(!is.na(lowest_rank),!is.na(highest_rank))%>%
  mutate(rank_diff=lowest_rank-highest_rank)
```

We could see that same university has different spelling in three ranking systems, resulting in NAs after the match.

#Visualize the difference
```{r}
diff=ggplot(RankDiff,aes(RankDiff$lowest_rank,RankDiff$highest_rank,color=country))+
  xlim(0,250)+ylim(0,250)+
  geom_point()+geom_abline(slope=1,intercept=0)+
  ggtitle('Max vs Min Rankings')+
  theme_fivethirtyeight()
```

The further away from the line, the bigger the difference between lowest rank and highest rank. Universities from Austria, Sweden, Denmark have a bigger variance

US not only has the most universities in the ranking, but also many with small variance across 3 systems

Next we view these universities one by one 
```{r, fig.width=10, fig.height=16}
RankDiff%>%
    ggplot(aes(institution)) +
    geom_linerange(aes(ymin = highest_rank, ymax = lowest_rank,color=country)) + 
    geom_point(aes(y = highest_rank, color=country)) +
    geom_point(aes(y = lowest_rank, color=country)) + 
    theme(
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank())+
    theme_classic()+coord_flip()
```

For all 3 rankings, what are their number of top 100 universities by country?
```{r warning=FALSE}

Top100bycountry<-function(x) {
  result=x%>%
    mutate(cntry=school_and_country_table$country[match(university_name,school_and_country_table$school_name)])%>%
    filter(year==yr)%>%
  head(100)%>%
  group_by(cntry)%>%
  tally()
  return(result)
}

colnames(cwurData)[2] <- "university_name"

cwur100=cwurData%>%Top100bycountry()
times100=timesData%>%Top100bycountry()
shanghai100=shanghaiData%>%Top100bycountry()

p1=merge(cwur100,times100,by="cntry",all=TRUE)
p2=merge(p1,shanghai100,by="cntry",all=TRUE)
names(p2)=c("cntry","cwur_n","times_n","shanghai_n")
p2%>%melt()%>%
  filter(!is.na(cntry))%>%
  ggplot(aes(cntry,value,fill=cntry))+
  geom_bar(stat="identity")+coord_flip()+facet_wrap(~variable)+
  geom_text(aes(label=value),nudge_y=2)+
  theme_fivethirtyeight()+
  ggtitle("Top 100 universities by country")+
  guides(fill=FALSE)
```

And the animated version to show it across years
```{r warning=FALSE}
saveGIF(
{
    for (i=2012) {
   
      Top100bycountry<-function(x) {
        result=x%>%
          mutate(cntry=school_and_country_table$country[match(university_name,school_and_country_table$school_name)])%>%
          filter(year==yr)%>%
        head(100)%>%
        group_by(cntry,year)%>%
        tally()
        return(result)
      }

colnames(cwurData)[2] <- "university_name"

cwur100=cwurData%>%Top100bycountry()
times100=timesData%>%Top100bycountry()
shanghai100=shanghaiData%>%Top100bycountry()

p1=merge(cwur100,times100,by=c("cntry","year"),all=TRUE)
p2=merge(p1,shanghai100,by=c("cntry","year"),all=TRUE)
names(p2)=c("cntry","year","cwur_n","times_n","shanghai_n")
plt=p2%>%melt(id=c("cntry","year"))%>%
  filter(!is.na(cntry))%>%
  ggplot(aes(cntry,value,fill=cntry))+
  geom_bar(stat="identity")+coord_flip()+facet_wrap(~variable)+
  geom_text(aes(label=value),nudge_y=2)+
  theme_fivethirtyeight()+
  ggtitle("Top 100 universities by country")+
  guides(fill=FALSE)
print(plt)

    }
}
, movie.name = "gifname_.gif", interval = runif(30, 0.01, 1), nmax = 30,
ani.width=850, ani.height=500)
```
