---
title: "scientific_migration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=F, warning=F)
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(RColorBrewer)
library(plotly) #contain hex to RGB conversion
#date
library(lubridate)
#geocode
library(countrycode)
#text
library(tidytext)
#forbes
library(forbesListR)
#theme
my_theme <- function(base_size = 12, base_family = "Helvetica"){
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    plot.title = element_text(face="bold", size=16),
    axis.text = element_text(face="bold"),
    plot.background = element_rect(fill = 'ghostwhite',color='white'),
    legend.position = 'None', legend.title = element_blank(),
    panel.grid.major = element_blank(), panel.grid.minor = element_blank())
}

```

## Load data

```{r input}
scientific_migration <- read_csv("~/git_repo/opendata_viz/scientific_migration/scientific_migration.csv")
```

```{r pre_process}

#replace long country names with show ones

replace = function(x, to_replace, replacement){
  ifelse(grepl(to_replace,x),replacement,x)
}


migrated_original <- scientific_migration %>%
  filter(!is.na(earliest_country), !is.na(country_2016)) %>%
  mutate(earliest_country_nm = countrycode(earliest_country, 'iso2c', 'country.name'),
         earliest_continent = countrycode(earliest_country, 'iso2c', 'continent'),
         latest_country_nm = countrycode(country_2016, 'iso2c', 'country.name'),
         latest_continent = countrycode(country_2016, 'iso2c', 'continent'),
         phd_country_nm = countrycode(phd_country, 'iso2c', 'country.name')) %>%
  mutate(earliest_country_nm = replace(earliest_country_nm, 'United Kingdom','UK')) %>%
  mutate(earliest_country_nm = replace(earliest_country_nm, 'United States','US')) %>%
  mutate(earliest_country_nm = replace(earliest_country_nm, 'Venezuela','Venezuela')) %>%
  mutate(earliest_country_nm = replace(earliest_country_nm, 'Iran','Iran')) %>% 
  mutate(earliest_country_nm = replace(earliest_country_nm, 'Taiwan','Taiwan')) %>% 
  mutate(latest_country_nm = replace(latest_country_nm, 'United Kingdom','UK')) %>%
  mutate(latest_country_nm = replace(latest_country_nm, 'United States','US')) %>%
  mutate(latest_country_nm = replace(latest_country_nm, 'Venezuela','Venezuela')) %>%
  mutate(latest_country_nm = replace(latest_country_nm, 'Iran','Iran')) %>%
  mutate(latest_country_nm = replace(latest_country_nm, 'Taiwan','Taiwan')) %>%
  mutate(migrated = ifelse(has_migrated == "True" & earliest_country!=country_2016, 1, 0))

#remove where od countries are the same
migrated <- migrated_original  %>%
  filter(migrated == 1)
```

## circular network of earliest - latest continents
```{r}
migrated_continents <- migrated %>%
  count(earliest_continent, latest_continent) %>% 
  filter(!is.na(earliest_continent), !is.na(latest_continent))
#very few records with na continent

grid.col = c(Asia = "#1B9E77", Europe = "#D95F02", Africa = "#7570B3",
             Americas = "#E7298A", Oceania = "#66A61E")
chordDiagram(migrated_continents, 
             directional = 1, 
             diffHeight  = -0.04,
             grid.col=grid.col)
```

## what % are intra-continent movement?

## for those intra-continent movement, what are the countries?

```{r}
migrated_intra <- migrated %>%
  filter(earliest_continent==latest_continent) %>%
  count(earliest_continent, earliest_country_nm, latest_country_nm)
```

```{r functions}
find_top_n = function(df, n) {
  top_orig <- df %>% count(earliest_country_nm, sort=T) %>% head(n)
  top_dest <- df %>% count(latest_country_nm, sort=T) %>% head(n)
  top_od <- union(top_orig$earliest_country_nm, top_dest$latest_country_nm)
  #col <- brewer.pal(length(top_od),"Dark2")
  df <- df %>% 
  mutate(earliest = ifelse(earliest_country_nm %in% top_od, earliest_country_nm,'others'),
         latest = ifelse(latest_country_nm %in% top_od, latest_country_nm,'others'))
}

region_summarize = function (df, i) {
  df %>% 
  find_top_n(i) %>%
  group_by(earliest, latest) %>%
  summarize(total = sum(n))
}

chord = function (df) {
  chordDiagram(region_summarize(df), 
             directional = 1, 
             diffHeight  = -0.04)
}
```

```{r}
migrated_intra %>% 
  filter(earliest_continent=='Africa') %>% 
  chord()
```
## Inter-continental movements on map

```{r}
migrated_inter <- migrated %>%
  filter(earliest_continent!=latest_continent) %>%
  count(earliest_country_nm, latest_country_nm) %>% 
  region_summarize(10)
write.csv(migrated_inter, 'migrated_inter.csv')
```

## outbound-inbound ratio,
normalize by total researcher population 
```{r}
ob_ratio = migrated_original %>% 
  group_by(earliest_country_nm) %>% 
  summarize(ob_ratio = mean(migrated), ob=sum(migrated)) %>%
  rename(cntry=earliest_country_nm)

ib_ratio = migrated_original %>% 
  group_by(latest_country_nm) %>% 
  summarize(ib_ratio = mean(migrated), ib=sum(migrated))%>%
  rename(cntry=latest_country_nm)

od <- ib_ratio %>% inner_join(ob_ratio) %>%
  mutate(ob_ib_ratio = ob/ib, total = ob+ib) %>%
  filter(mean(total) < total) #overall movement above avg
```
higest
```{r}
s=od%>%arrange(desc(ob_ib_ratio)) %>% head(10)
ggplot(s) +
  geom_point(aes(reorder(cntry, -ob_ib_ratio), ob_ib_ratio+s$ob_ratio/0.75), 
             shape=24, fill="green", size=s$ob_ratio/0.05, alpha=0.9) +
  geom_point(aes(reorder(cntry, -ob_ib_ratio), ob_ib_ratio+s$ib_ratio/0.75), 
             shape=25, fill="brown", size=s$ib_ratio/0.05, alpha=0.5) + 
  my_theme() + 
  labs(title='Highest outbound/inbound ratio in researcher migration',
caption = 'Source: ORCID')
```

lowest
```{r}
#need better ways to adjust height
s=od%>%arrange(desc(ob_ib_ratio)) %>% tail(10)
ggplot(s) +
  geom_point(aes(reorder(cntry, ob_ib_ratio), ob_ib_ratio), 
             shape=24, fill="green", size=s$ob_ratio/0.05, alpha=0.5) +
  geom_point(aes(reorder(cntry, ob_ib_ratio), ob_ib_ratio-s$ib_ratio/30), 
             shape=25, fill="brown", size=s$ib_ratio/0.05, alpha=0.6) + 
  my_theme() + 
  labs(title='Lowest outbound/inbound ratio in researcher migration',
caption = 'Source: ORCID')
```


## phD country
Since there are too many countries, at country level we find top 10 and group others
origin here is the earliest country the researcher has recorded activity, which doesn't equal home country

```{r}
migrated <- migrated %>% 
         mutate(phd_cntry_type = ifelse(phd_country_nm==earliest_country_nm, 'same as earliest',
                                 ifelse(phd_country_nm==latest_country_nm, 'same as latest','others')))
```

what % had phd in origin country? dest country? yet another country? 
which continent is it on?
what % have o-d in the same region? continent?

```{r}
prop.table(table(migrated$phd_cntry_type))
```
49% had phd in the earliest country, 39% had it in their migrated country, 12% had it elsewhere


```{r marimekko}
#make mosaic plot 
df <- migrated %>%
  group_by(earliest_continent, phd_cntry_type) %>%
  summarise(count = n()) %>%
  na.omit() %>%
  mutate(cut.count = sum(count),
         prop = count/sum(count)) %>%
  ungroup()

ggplot(df,
       aes(x = earliest_continent, y = prop, width = cut.count, fill = phd_cntry_type)) +
  geom_bar(stat = "identity", position = "fill", colour = "black") +
  coord_flip() +
  facet_grid(earliest_continent~., scales = "free_x", space = "free_x") +
  scale_fill_brewer(palette = "Dark2") +
  theme_void() + 
  theme(strip.text.y = element_text(angle=0), legend.position = 'bottom')
```


