---
title: "Visualization data visualization"
output: 
    html_document: 
      toc: true
---

```{r message=FALSE, warning=FALSE, echo=FALSE}

library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(dplyr)
library(reshape2)
library(tidyr)
library(formattable)
library(RColorBrewer)
library(lubridate)
library(plotly)
library(viridis)
library(ggthemes)

```

```{r message=FALSE}
#data from https://github.com/emeeks/data_visualization_survey/blob/master/data/cleaned_survey_results.csv
df<- read_csv("~/git_repo/Dataviz_survey/dataviz_survey.csv")
```

```{r check}
sum(sapply(df, is.numeric))
sum(sapply(df, is.character))
```
```{r}
colnames(df) <- c("ts", "years_in_dataviz","education","how_to_learn","how_to_start",
                   "first_job","job_title","compensation","proportion",
                   "hired_for_dataviz","job_status","how_is_dataviz_used",
                   "team_structure","usage","leadership_role","department",
                   "pct_dv","pct_de","pct_ds","pct_design","pct_prep",
                   "tool","tool_origin","how_to_present","chart_type",
                   "audience","fluency","frequency_usage","purpose","relation",
                   "frustration","frustration_dataviz","what_to_change",
                   "what_to_change_dataviz","ppl_dont_get_it",
                   "how_to_make_job_better","what_to_expect","viz_hero",
                   "time_spent_in_future","gender","age","location",
                   "race","sector")
```

```{r}
summary(df)
```
```{r}
lapply(df[,22:30], table) #apply to all character col
```
#demographics
```{r}
demographics <- df %>%
  group_by(years_in_dataviz, education, job_status, gender, age, location, race, sector) %>%
  summarize(n = n())
write.csv(demographics, "datavizdemographics.csv")
#input to raw density for nice sankey chart to view multiple dimension at once
```
The surveyed is heavily focused on North America, followed by Europe; mostly male.Most of the surveyed use data visualization for part of the job, only 21% are hired for data visualization.
It has a good representation of both fresh grad and experienced professional; and reasonably covers private and public sectors as well as academic.

```{r}
# i='education'
# df %>% #select(i) %>%
# #   mutate_(i = strsplit(i,";")) %>%
# #            unnest()%>% filter(!is.na(i)) %>%
#   group_by_(i) %>% summarize(n=n()) %>%
#   arrange(desc(n)) %>% head(20) %>%
#   ggplot(aes(i, n)) + geom_bar(stat="identity") + coord_flip() +
#   theme_bw()
```

#favorite charttype
```{r}
chart_type <- df %>% select(chart_type, education,how_to_learn,first_job,
                   job_status,hired_for_dataviz,gender,age,location,
                   race,sector) %>%
  mutate(chart_type = strsplit(chart_type,";")) %>%
           unnest()
chart_type %>% filter(!is.na(chart_type)) %>%
  group_by(chart_type) %>% summarize(n=n()) %>%
  arrange(desc(n)) %>% head(20) %>%
  ggplot(aes(reorder(chart_type, n), n)) + geom_bar(stat="identity") + coord_flip() +
  theme_tufte() + 
  theme(axis.title.y=element_blank(),axis.title.x=element_blank(),
        panel.grid.major.x = element_line(colour = "grey"))
```
#Who are the purpose
```{r audience}
audience <- df %>% select(audience, education,how_to_learn,first_job,
                   job_status,hired_for_dataviz,gender,age,location,
                   race,sector) %>%
  mutate(audience = strsplit(audience,";")) %>%
           unnest() %>%
  filter(!is.na(audience)) %>%
  group_by(audience) %>% 
  summarize(n=n())
audience_top8 <- audience %>% 
  arrange(desc(n)) %>% head(8) 
audience%>%
  mutate(audience = ifelse(audience %in% audience_top8$audience, audience,"others"))%>%
  ggplot(aes(reorder(audience, n), n)) + geom_bar(stat="identity") + coord_flip() +
  theme_tufte() + 
  theme(axis.title.y=element_blank(),axis.title.x=element_blank())
```

```{r how_to_present}
how_to_present <- df %>% select(how_to_present, education,how_to_learn,first_job,
                   job_status,hired_for_dataviz,gender,age,location,
                   race,sector) %>%
  mutate(how_to_present = strsplit(how_to_present,";")) %>%
           unnest() %>%
  filter(!is.na(how_to_present)) %>%
  group_by(how_to_present, hired_for_dataviz) %>% 
  summarize(n=n()) %>%
  arrange(desc(n)) %>%
  ungroup()
how_to_present_top7 = how_to_present%>% head(7) 
how_to_present %>% 
  mutate(how_to_present = ifelse(how_to_present %in% how_to_present_top7$how_to_present, how_to_present,"others")) %>% 
  ggplot(aes(reorder(how_to_present, n), n)) + geom_bar(stat="identity") + 
  coord_flip() +
  theme_tufte() + 
  theme(axis.title.y=element_blank(),axis.title.x=element_blank()) +
  facet_wrap(~hired_for_dataviz)
```
```{r usage}
how_is_dataviz_used <- df %>% select(how_is_dataviz_used, education,how_to_learn,first_job,
                   job_status,hired_for_dataviz,gender,age,location,
                   race,sector) %>%
  mutate(how_is_dataviz_used = strsplit(how_is_dataviz_used,";")) %>%
           unnest()
how_is_dataviz_used %>% filter(!is.na(how_is_dataviz_used)) %>%
  group_by(how_is_dataviz_used) %>% summarize(n=n()) %>%
  arrange(desc(n)) %>% head(10) %>%
  ggplot(aes(reorder(how_is_dataviz_used, n), n)) + geom_bar(stat="identity") + 
  coord_flip() +
  theme_tufte() + 
  theme(axis.title.y=element_blank(),axis.title.x=element_blank())
```

#viz gurus
```{r}
# common_fields <- c("education","how_to_learn","first_job",
#                    "job_status","hired_for_dataviz","gender","age","location",
#                    "race","sector")
guru <- df %>% select(viz_hero, education,how_to_learn,first_job,
                   job_status,hired_for_dataviz,gender,age,location,
                   race,sector) %>%
  mutate(guru = strsplit(viz_hero,";")) %>%
           unnest()
guru %>% filter(!is.na(guru)) %>%
  group_by(guru) %>% summarize(n=n()) %>%
  arrange(desc(n)) %>% head(20) %>%
  ggplot(aes(reorder(guru, n), n)) + 
  geom_bar(stat="identity") + 
  coord_flip() +
  theme_tufte() + 
  theme(axis.title.y=element_blank(),axis.title.x=element_blank())
```
```{r howtolearn}
library(stringr)
df %>% filter(!is.na(hired_for_dataviz)) %>%
  ggplot(aes(str_wrap(how_to_learn,20), 
             str_wrap(hired_for_dataviz,22))) +
  geom_jitter(alpha=0.5) +
  theme_tufte() + 
  theme(axis.title.y=element_blank(),axis.title.x=element_blank(),
        #axis.text.x = element_text(angle=30,hjust=1,vjust=0.8)
        )
```

