---
title: "Shark Attack"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(dplyr)
library(reshape2)
library(formattable)
library(RColorBrewer)
library(ggthemes)
library(tidytext)
library(lubridate)
attacks <- read_csv("attacks.csv")
```

###Preprocessing
```{r  message=FALSE, warning=FALSE, echo=FALSE}

attacks <- attacks %>%
  mutate(Date = dmy(Date))%>%
mutate(fatality=ifelse(`Fatal (Y/N)`=='Y',1,0))%>%
mutate(Injury_Type = ifelse(
  is.na(Injury), "NA",
  ifelse(grepl("bitten", Injury, ignore.case = T),"Bitten",
  ifelse(grepl("Laceration", Injury, ignore.case = T), "Lacerations", 
  ifelse(grepl("Minor injury", Injury, ignore.case = T), "Injured",
  ifelse(grepl("Injured", Injury, ignore.case = T), "Injured",
  ifelse(grepl("Injuries", Injury, ignore.case = T), "Injured",
  ifelse(grepl("No injury", Injury, ignore.case = T), "No Injury",
  ifelse(grepl("Disappeared", Injury, ignore.case = T), "Disappeared",      
  ifelse(grepl("FATAL", Injury, ignore.case = T), "Fatal", "Others")))))))))) %>%
mutate(Activity_Type = ifelse(
  is.na(Activity),"NA",
  ifelse(grepl("Surf.*", Activity, ignore.case = T),"Surfing",
  ifelse(grepl("Swim.*", Activity, ignore.case = T), "Swimming", 
  ifelse(grepl("Fishing", Activity, ignore.case = T), "Fishing",
  ifelse(grepl("Bath.*", Activity, ignore.case = T), "Bathing",
  ifelse(grepl("Wading", Activity, ignore.case = T), "Wading",
  ifelse(grepl("Diving", Activity, ignore.case = T), "Diving",
  ifelse(grepl("Standing", Activity, ignore.case = T), "Standing",      
  ifelse(grepl("Snorkel+ing", Activity, ignore.case = T), "Snorkelling", "Others"))))))))))
```

##Visualize by attack scenarios

```{r message=FALSE, warning=FALSE, echo=FALSE, fig.width=6, fig.height=4}
attacks %>%
  count(Type, sort=T) %>%
  mutate(Type=reorder(Type,n))%>%
  ggplot(aes(Type,n)) +
  geom_bar(stat='identity',color='white') + 
  coord_flip() +
  geom_text(aes(label=n,hjust=-0.1)) + 
  theme_minimal() + 
  ggtitle('Shark Attack Scenarios') 
```

##Visualize by top activities

```{r message=FALSE, warning=FALSE, echo=FALSE, fig.width=6, fig.height=4}
attacks %>%
  count(Activity_Type, sort=TRUE) %>%
  mutate(Activity_Type=reorder(Activity_Type,n))%>%
  ggplot(aes(Activity_Type,n)) +
  geom_bar(stat='identity',color='white') + 
  coord_flip() +
  geom_text(aes(label=n,hjust=-0.1)) + 
  theme_minimal() + 
  theme(axis.text=element_text(size=16)) +
  ggtitle('Shark Attack by Activities') 

```

Surfing, Swimming and Fishing appear to be the main triggering activities, let's figure out what's in the others (which got covered up in the sentences) by tokenize them

```{r message=FALSE, warning=FALSE, echo=FALSE, fig.width=6, fig.height=6}
library(tidytext)
attacks%>%
  filter(Activity_Type=='Others')%>%
  select(Activity)%>%
  unnest_tokens(Word, Activity)%>% 
  anti_join(stop_words, c(Word = "word")) %>%
  count(Word, sort = TRUE)%>%
  mutate(Word=reorder(Word,n))%>%
  head(50)%>%
  ggplot(aes(Word, n)) +
  geom_bar(stat = "identity") + 
  coord_flip() + 
  geom_text(aes(label=n,hjust=-0.1)) + 
  theme_minimal() 
```

From this chart we can see there's no other activities with more incident than snorkelling, so we can safely store them in 'others' bucket.


##Visualize by injury type


```{r message=FALSE, warning=FALSE, echo=FALSE, fig.width=6, fig.height=4}
attacks %>%
  count(Injury_Type, sort=TRUE) %>%
  mutate(Injury_Type=reorder(Injury_Type,n))%>%
  ggplot(aes(Injury_Type,n)) +
  geom_bar(stat='identity',color='white') + 
  coord_flip() +
  geom_text(aes(label=n,hjust=-0.1)) + 
  theme_minimal() + 
  theme(axis.text=element_text(size=16)) +
  ggtitle('Shark Attack by Injury Type') 
  
```

##What's the relation between activity and injury?

```{r message=FALSE, warning=FALSE, echo=FALSE, fig.width=4.6, fig.height=4.6}
attack_activity_injury <- attacks %>%
  group_by(Activity_Type, Injury_Type)%>%
  summarize(count=n(), fatality_rate=sum(fatality, na.rm=TRUE)/n())
attack_activity_injury%>%
  ggplot(aes(Activity_Type, Injury_Type)) + 
  geom_point(aes(size = count, colour=fatality_rate)) + 
  scale_colour_gradientn(colours=c("#88d8b0","#ff6f69")) + 
  ggtitle("Shark attack incidences by activity and injury type") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme_minimal() + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
  theme(axis.title.y=element_blank(),axis.title.x=element_blank(), legend.position="right")
```
## And exactly where in the world do those attacks occur? 
```{r}
attack_by_top_country <- attacks %>%
  count(Country,sort=TRUE)%>%
  head(100)
attack_by_top_country
```
Get their geocode and do something big

```{r}
attack_by_country <- attacks %>%
  filter(!is.na(Country))%>%
   group_by(Country,Year, Activity_Type, fatality) %>%
   summarize(n = n())
# geocodes <- geocode((attack_by_country$Country))
# geolocation <-data.frame(attack_by_country,geocodes)
```


```{r message=FALSE, warning=FALSE, echo=FALSE}
library(leaflet)
library(ggmap)
attack_by_country <- attacks %>%
  filter(!is.na(Country))%>%
  count(Country,sort=TRUE)
geocodes <- geocode((attack_by_country$Country))
geolocation <-data.frame(attack_by_country[,1:2],geocodes)
geolocation%>%
  leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolygons(lng = ~lon, lat = ~lat, 
             popup = ~Country, fillColor = ~n)
```


How do shark attacks vary over the year
```{r message=FALSE, warning=FALSE, echo=FALSE, fig.width=4.6, fig.height=3}
attacks %>%
  filter(Year>1800, Country%in%attack_by_country$Country)%>%
  group_by(Year, Country, fatality)%>%
  summarize(count=n())%>%
  ggplot(aes(Year,count, color=factor(fatality))) +
  geom_point(size=1, alpha=0.6) + 
  facet_wrap(~Country) +
  ggtitle("Shark Attack over the Years") + theme_minimal() +
  theme(legend.position="right",axis.text.x=element_text(angle=90))
```
Most shark attacks occur in USA and Australia, there has been a peak in 1960s, then growing number of incidents in recent years


