---
title: "Who to fly with"
output: html_document
---

In this analysis we'll analysis 45K skytrax review:

* Do airlines form clusters, if so, is it similar to their alliances?
* Do people prefer their national/region airlines more so than others?


```{r setup, include=FALSE,warning = FALSE, error = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(Hmisc)
#text
library(tidytext)
library(cleanNLP)
init_spaCy(model_name = "en")
#machine learning
library(caret)
#dataviz
library(ggplot2)
library(igraph)
library(ggraph)
library(RColorBrewer)
library(ggalt)
library(ggthemes)
library(ape)
library(d3heatmap)
library(fmsb)
```

#Pre-processing

```{r input, warning = FALSE, error = FALSE, message=FALSE}
#source https://github.com/quankiquanki/skytrax-reviews-dataset
#airline by country:http://www.nationsonline.org/oneworld/major_airlines.htm
#more airline by country: https://en.wikipedia.org/wiki/List_of_passenger_airlines
airline <- read_csv("~/git_repo/opendata_viz/skytrax/airline.csv")
```

```{r pre_process}
airline <- airline %>%
  mutate(date = ymd(date), year = year(date)) %>%
  filter(year > 2000)
```

we can see the review started in 2002 (1970 got to be an error, Skytrax wasn't even founded then) and 2015 isn't a full year at the time of data collection

#Part 1: EDA

```{r}
# df_recommend <- airline %>% 
#   group_by(airline_name) %>%
#   summarize(pct_recommend = mean(recommended), n_reviewed = n()) 
```

```{r}
df_country <- airline %>% 
  filter(!is.na(author_country))%>% 
  group_by(author_country) %>%
  count(sort = T) 

#top 15 reviewer country
df_country20 <- df_country%>%
  head(15)
```

```{r}
#top 20 airline
df_airline_20 <- airline %>% 
  filter(!is.na(airline_name))%>% 
  group_by(airline_name) %>%
  count(sort = T) %>%
  head(20)
```


```{r 15rankingbycountry}
#among airlines with more than median amount of review, choose the most recommended
df_country_recommend <- airline %>%
  filter(author_country %in% df_country20$author_country) %>%
  group_by(airline_name, author_country) %>%
  dplyr::summarize(pct_recommend = mean(recommended), n_reviewed = n()) %>%
  ungroup %>%
  group_by(author_country) %>%
  mutate(mean_reviewed = mean(n_reviewed)) %>%
  filter(n_reviewed >= mean_reviewed) %>%
  arrange(desc(n_reviewed),desc(pct_recommend)) %>%
  slice(1:3)
```

```{r}
df_country_recommend$author_country = factor(df_country_recommend$author_country, levels = df_country20$author_country)
levels(df_country_recommend$author_country)
```

The 3 most reviewed airlines and their ratings by passenger country
```{r}
#diverging palette need discrete scale
df_country_recommend %>%
  mutate(if_recommend = ifelse(pct_recommend >= 0.8, 2, 
                             ifelse(pct_recommend >= 0.6, 1,  
                                    ifelse(pct_recommend >=0.4, 0,  
                               ifelse(pct_recommend >= 0.2,-1, -2))))) %>%
  ggplot(aes(reorder(airline_name, n_reviewed), n_reviewed)) +
  geom_bar(stat = 'identity', 
           aes(fill= as.factor(if_recommend)), width=0.2) + 
  coord_flip() +
  facet_wrap(~author_country, ncol=3, scales = "free_y") + 
  theme_economist() + 
  theme(axis.title = element_blank(),
        plot.title = element_text(face="bold", size=16),
        legend.position = "None",
        panel.grid.major.y=element_blank(),
        axis.line=element_blank(),
        axis.text.y  = element_text(hjust=1)
        ) +
  labs(title = "Favorite Airlines by Reviewers' Country",
       subtitle = "Ranked by number of reviews, colored by percent of positive reviews", 
       caption = "Source: Skytrax") +
  scale_fill_brewer( palette = "PiYG") 
   
```


Compare the review on each sub-category
```{r sub-cat}
df_airline_30 <- airline %>% 
  filter(!is.na(airline_name))%>% 
  group_by(airline_name) %>%
  count(sort = T) %>%
  head(30)

df_subcat <- airline %>%
  filter(airline_name %in% df_airline_30$airline_name) %>%
  dplyr::select(airline_name, seat_comfort_rating:value_money_rating) %>%
  group_by(airline_name) %>%
  summarise_all(mean,na.rm=TRUE) %>%
  na.omit()
#%>% gather(key, value, -airline_name)
#write.csv(df_subcat, 'df_subcat.csv')
```


#PART 2: Clustering
##which airlines are similar in subcategory
```{r}
#for showing labels on dendrogram it's necessary to have them as row.name of the dataframe
df_subcat=as.data.frame(df_subcat)
row.names(df_subcat)=df_subcat$airline_name

cols<-brewer.pal(n=6,name="Dark2")

#hierarchical clustering
hc=hclust(dist(df_subcat, method='euclidean'), 
          method='ward.D2')

plot(as.phylo(hc), type = "cladogram", cex = 0.9, tip.color = cols[cutree(hc,6)])
```

```{r radar}
#remove rating from colnames
colnames(df_subcat) = gsub("_rating", "", colnames(df_subcat))
#add class label to df
 cls = as.data.frame(cutree(hc,6))
 cls$airline_name=row.names(cls)
 df_subcat = df_subcat %>%
   left_join(cls)

 i=1
 for( i in (1:6)){
  #mypath <- file.path(paste0("myplot_", i, ".png"))
  png(file=paste0("myplot_", i, ".png"))
  df_sub=df_subcat %>% filter(`cutree(hc, 6)`==i)
  df_sub=rbind(rep(5,7) , rep(0,7) , df_sub)
  radarchart((df_sub[,2:8]), pcol=cols[i], 
             plwd=2, cglcol="lightgrey")
  dev.off()
}
```

##correlation between categorical rating and overall rating
```{r corr}

df_corr <- airline[,c(1,12:19)] %>%
  group_by(airline_name)%>%
  summarize_all(mean,na.rm=TRUE) 
#colnames(df_corr) = gsub("_rating", "", colnames(df_corr))
colnames(df_corr) = c('airline_name','overall','seat','cabin','food','movie','ground','wifi','value')
row.names(df_corr) <- df_corr$airline_name
df_corr <- df_corr %>% na.omit()
library(corrplot)
corrcol <-brewer.pal(n=6,name="YlGnBu")
par(cex = 0.7)
M <- cor(df_corr[,2:9])
corrplot.mixed(M, col=corrcol)
```



#PART 3: NLP
```{r}
#limit to 1 year
# airline15=airline %>% filter(year==2015, airline_name %in% df_airline_30$airline_name)
# anno <- run_annotators(airline15$content, as_strings = TRUE)
# nlp <- get_combine(anno)
```

```{r}
# airline15_idex <- airline15 %>%
#   mutate(id = row_number()) %>% 
#   dplyr::select(id, airline_name, recommended, year)
# 
# 
# token <- nlp %>% 
#   # filter(upos=='ADJ', pos=='JJ', 
#   #              lemma!='other', lemma_source!='be') %>%
#   left_join(airline15_idex) %>%
#   group_by(id, year, recommended) %>%
#   dplyr::summarize(review_length = n())

# token %>%
#   ggplot(aes(as.factor(recommended), review_length))+
#   geom_boxplot()
```
