---
title: "How people learn to code"
output: 
    html_document: 
      toc: true
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
# This is a code block
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(dplyr)
library(reshape2)
library(tidyr)
library(formattable)
library(RColorBrewer)
library(lubridate)
library(plotly)
library(viridis)

```

```{r message=FALSE}
df<- read.csv("~/R/Kaggle_Dataset/CodeCamp.csv", stringsAsFactors=FALSE)
glimpse(df)
```
#Demographics
Some basic demographics: gender and age mix
```{r warning=FALSE, message=FALSE ,echo=FALSE}
df%>%select(Age, Gender)%>%
group_by(Age, Gender)%>%
summarize(count=n())%>%
ggplot(aes(Age,count,fill=Gender))+
geom_bar(stat='identity',position='stack',color='white')+theme_classic()
```

The surveyed has median age of 27, more male than female

Let's see if the gender mix change across ages
```{r warning=FALSE , message=FALSE ,echo=FALSE}
df%>%select(Age, Gender)%>%
group_by(Age, Gender)%>%
summarize(count=n())%>%
ggplot(aes(Age,count,fill=Gender))+
geom_bar(stat='identity',position='fill',color='white')+xlim(c(10,70))+
theme_classic()
```
There are increasing percentage of older female coding.

What are the top countries people live in

```{r echo=FALSE}
topcntry=df%>%select(CountryLive)%>%
group_by(CountryLive)%>%
filter(!is.na(CountryLive))%>%
summarize(ncount=n())%>%
arrange(desc(ncount))%>%
head()%>%
select(CountryLive)

df$CityPopulation=factor(df$CityPopulation,levels=c("less than 100,000","between 100,000 and 1 million","more than 1 million"))

df%>%select(CountryLive,CityPopulation )%>%
filter(CountryLive%in%as.list(topcntry)[[1]])%>%
filter(!is.na(CityPopulation))%>%
group_by(CountryLive, CityPopulation )%>%
summarize(ncount=n())%>%
spread(CityPopulation,ncount)%>%
formattable()
```

Based on residential country, 46% of the surveyed live in US
36% are from cities with between 100K to 1M people, while 40% are from big cities with more than 1 milion people.

#Socio-economic profile
The surveyed has median income of 37K, minimally 6K, maximally 20K.

In terms of hours of learning, how are people of different income group behave differently?
```{r echo=FALSE, warning=FALSE}
df%>%
  mutate(Incomecut=cut(Income,seq(0,200000,50000)))%>%
  select(HoursLearning,Incomecut)%>%
  filter(!is.na(Incomecut))%>%
  ggplot(aes(HoursLearning,fill=Incomecut))+geom_density(alpha=0.5)+
  facet_wrap(~Incomecut,nrow=2)+
  ggtitle('Learning hours by income group')+theme_classic()
```


#Career
67 % of those attended bootcamp finished them.  58 % of those finish bootcamp had full-time job afterwards.
```{r echo=FALSE, message=FALSE}
paste(round(sum(df$BootcampFinish,na.rm=TRUE)/sum(df$AttendedBootcamp,na.rm=TRUE),2)*100, "%of those attended bootcamp finished them. ", round(sum(df$BootcampFullJobAfter,na.rm=TRUE)/sum(df$BootcampFinish,na.rm=TRUE),2)*100, "% of those finish bootcamp had full-time job afterwards. Some of the rest may not have filled survey")
```
What are the job fields and employment status for participant
```{r echo=FALSE}
df%>%
  filter(AttendedBootcamp==1)%>%
  select(EmploymentField,EmploymentStatus)%>%
  filter(!is.na(EmploymentField),!is.na(EmploymentStatus))%>%
  group_by(EmploymentField,EmploymentStatus)%>%
  summarize(ncount=n())%>%
  arrange(ncount)%>%
  ggplot(aes(EmploymentField,ncount,fill=EmploymentStatus))+
  geom_bar(stat='identity',position='stack',color='white')+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
  ggtitle('Employment status and field among Bootcamp participants')+
  coord_flip()+theme_classic()
```

Majority are employed for wages and working in software development and IT. Participants also come from in sales, education, finance, media etc.

Next we'll how are people's current job differ from their ideal job
```{r echo=FALSE}
as.data.frame(table(df$EmploymentStatus,df$JobPref))%>%
  select(current=Var1,ideal=Var2,Freq)%>%
  ggplot(aes(ideal, current))+
  geom_tile(aes(fill = Freq), colour = "white")+
  scale_fill_viridis()+ 
  coord_fixed(ratio = 1)+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```

So lots of people employeed for wages want changes, either work for a medium-sized company, or start-up, freelance, etc


#Online Resources for learning coding
Let's see what resources they use to learn online
```{r echo=FALSE}
online=df%>%select(matches('Resource'))%>%
  select(-ResourceOther)
data.frame(name=substring(names(online),9), #extract names
                        count=colSums(online,na.rm=TRUE),row.names=NULL)%>%
  arrange(desc(count))%>%
  formattable(list(count = color_bar("lightgreen",0)),
    align = 'l')
```

It appears Freecodecamp, Codeacademy, Udemy, Udacity, Coursera, Edx, Khan Academy and PluralSight are among popular resources

#Coding Events
Next let's see what Code events people join

```{r echo=FALSE, message=FALSE}
codeevent=df%>%select(matches('CodeEvent'))%>%
  select(-CodeEventOther)
data.frame(name=substring(names(codeevent),10), #extract names
                        count=colSums(codeevent,na.rm=TRUE),row.names=NULL)%>%
  arrange(desc(count))%>%
  formattable(list(count = color_bar("lightblue",0)),
    align = 'l')
```

It appears conference, coffee  and hackathon are among the top code events.

#Coding podcast
What podcast do they listen to?
```{r echo=FALSE, message=FALSE}
podcast=df%>%select(matches('Podcast'))%>%
  select(-PodcastOther)
data.frame(name=substring(names(podcast),8), #extract names
                        count=colSums(podcast,na.rm=TRUE),row.names=NULL)%>%
  arrange(desc(count))%>%
  formattable(list(count = color_bar("pink",0)),
    align = 'l')

```

JS Jabber, Code Newbie and SE Daily sounds fun

#Bootcamp
What are the bootcamps people attend and do people recommend it

```{r message=FALSE, echo=FALSE}
df%>%
  filter(!is.na(BootcampName))%>%
  select(BootcampName,BootcampRecommend)%>%
  filter(!grepl("Free Code", BootcampName))%>%
  group_by(BootcampName)%>%
  filter(!is.na(BootcampRecommend))%>%
  summarize(recommendpct=percent(sum(BootcampRecommend)/n(),digits=0),
            attendee=n())%>%
  arrange(desc(attendee),desc(recommendpct))%>%
  formattable(list(attendee= color_bar("lightblue",0),
            recommendpct=formatter("span",
    style = x ~ ifelse(x >=0.5, "color:green","color:red"))    
                   ), align = 'l')
```

GA has most attendees yet 22% don't recommend it, Flatiron comes next with high recommendation rate. This is an interesting list of bootcamps, useful for informing bootcamp attending decision as well

