
---
title: "Academic Tools"
output: html_document
---
```{r}
# to-do
# change tool abbre to full spelling
# add annotation to tool category
# normalize counts
# add relation between tools
# 
# questions:
#   most common tools by fields
#   shareability among fields
#   tools shared by fields
#   core tools unique to a fields
#   transferable skills: which discipline share unique tools
```


```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
library(formattable)
library(RColorBrewer)
library(tidyr)
library(viridis)
library(stringr)
#library(vcd)
col=rev(brewer.pal(10,'PiYG'))
survey_cleaned <- read.csv("academic_tools.csv", stringsAsFactors=FALSE)
variable_list <- read_csv("variable_list.csv")

```

```{r preprocessing}

survey_cleaned <- survey_cleaned %>%
  mutate(ROLE = ifelse(ROLE%in%c("PhD student","Postdoc"), "PhD/Postdoc",
                ifelse(grepl("prof",ROLE),"Professor",ROLE))) %>%
  mutate(PUBYEAR = as.factor(PUBYEAR), ROLE = as.factor(ROLE))
levels(survey_cleaned$PUBYEAR) = c("","before 1991","1991-2000","2001-2005","2006-2010","2011-2016","I haven't published (yet)")
levels(survey_cleaned$ROLE) = c("Bachelor/Master student", "PhD/Postdoc", "Professor", 
                         "Industry / Government","Librarian", "Publisher", "Other")
dict <- variable_list %>%
  separate(`full name / survey question`, c("question", "tool"), sep='-') %>%
  mutate(usage=ifelse(grepl("What tools/sites do you use to", question), 
                      substr(question, 31, nchar(question)), 
                      ifelse(grepl("What researcher profiles do you use", question),
                             "researcher profiles",
                             ifelse(grepl("reference management", question),
                                    "reference management",
                                    ifelse(grepl("peer review", question),
                                           "peer review", "")))))%>%
  select(field=`variable name`, usage, tool) 
```

Who were surveyed?
```{r role}
survey_cleaned%>%
  group_by(ROLE)%>%
  summarise(count=n())%>%
  arrange(desc(count))%>%
  formattable(
    list(count = color_bar("pink",0.1)),
    align = 'l') 
```
Anyone cross-disciplinary?
```{r crossdisciplinary}
quantify=function(x) ifelse(nchar(x) > 0, 1, 0)

survey=survey_cleaned%>%
  mutate_each(funs(quantify),PHYS:ARTHUM)%>%
  mutate(totalfield=rowSums(.[5:11])) 

prop.table(table(survey$totalfield))
```

83% work in one academic field while 17% are cross-disciplinary.  
And there are people crossing all 7 fields, including librarians and publishers

Next we study only single-field academics and consolidate all academic field to one column, and filter for professors as others may have uneven level of skills and tool usage
```{r}
survey=survey%>%
  filter(totalfield==1)
df2=survey%>%
  select(PHYS:ARTHUM)
whichfield=function(x) colnames(df2)[[which(x==1)]]
df2$field=apply(df2,1,whichfield)

#understand the field of the survey participant
df3=df2%>%
  select(-c(1:7))%>%
  bind_cols(survey)
  #filter(ROLE=='Professor / Associate professor / Assistant professor')
```

Which fields has the most records
```{r}
freqfield=df3%>%
  group_by(field, ROLE)%>%
  summarize(num=n())%>%
  arrange(desc(num))
```

Count number of tool usage
```{r usagewithinfield}
#freq to tool usage withint each field
toolset=df3%>%
  select(-matches("SPECCL")) %>%
  mutate_each(funs(quantify),GSCHOLSEARCH:IMPACTOTHCL) %>%
  select(c(field,ROLE, GSCHOLSEARCH:IMPACTOTHCL)) %>%
  group_by(field, ROLE ) %>%
  summarise_each(funs(sum)) %>%
  melt(id=c("field","ROLE")) %>%
  left_join(dict, by = c('variable' = 'field')) %>%
  left_join(freqfield,by=c('field','ROLE')) %>%
  mutate(freq=value/num) %>%
  na.omit() %>%
  select(1,2,5,6,7,8)
head(toolset)  
#note how to join on different col names in dplyr
```  
Visualize tools used by academic field

```{r,fig.width=12,fig.height=20}
#interaction(tool, usage, lex.order = TRUE)
png("tools.png", width = 1000, height = 2000)
ggplot(toolset, aes(field, tool)) + 
geom_tile(aes(fill = freq), colour = "white") +
facet_grid(str_wrap(usage,10)~ROLE, scales = "free_y", space = "free_y") +
scale_fill_viridis(option='C') + 
coord_fixed(ratio = 1) +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
theme(axis.title.y=element_blank(),axis.title.x=element_blank(), legend.position = 'None',
      axis.text.y = element_text(size=14),
      plot.title = element_text(face="bold",hjust = 0.5),
      strip.text.y = element_text(angle=0)) +
  ggtitle('Academic Tools by Disciplines and Roles')

dev.off()
```
```{r}
#temp=toolset%>%group_by(field,variable)%>%summarize(value=sum(value))
write.csv(temp,'temp.csv')
```

Prevalent tools used by all include word, Acrobat PDF Reader, Insitutional Access, Google Scholar. Excel is also common except in Law.  
Now to industry-specific tools:  
* PubMed is commonly used in Life science and Medicine.  
* ResearchGate is used by all but less often in Arts and Law.  
* Engineering use more Matlab than the rest, while Med and Social sciences use SPSS.
* Engineering and Physics uses more Latex.  
* Law uses SSRN relatively frequently, while Physics is the most frequent user of ARXIV.  

Lastly we look at their atitude towards open access and open science
```{r}
Attitude=df3%>%
    select(OPENSCI,OPENACC)%>%
    filter(OPENACC!=""&OPENSCI!='')%>%
    table()
mosaicplot(Attitude,color =brewer.pal(3,"PiYG"))
```
Majority are supportive of both, let's see who's opposing them
```{r}
naysayer=df3%>%
  filter(OPENACC=="No"&OPENSCI=='No')%>%
  select(PUBYEAR,field)%>%
  table()
tbl=cbind(naysayer=naysayer%>%colSums(),freqfield%>%group_by(field)%>%summarize(sum(num)))
tbl[1]/tbl[3]
```
Only 1-3% of professor from each field oppose the open initiative