---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(tidyr)
library(RColorBrewer)
library(sqldf)
library(ggraph)
library(igraph)
library(dplyr)
```

In this analysis we want to:

* understand of network of developper types/language/frameworks and evolution of it
  * Compare past and future skills
  * zoom in to data scientists

Load data

```{r input}
dev_survey <- read_csv("~/git_repo/opendata_viz/dev_survey/dev_survey.csv")
```



```{r pre_process}
df <- dev_survey %>%
  select_if(grepl("HaveWorked", names(.))|grepl("WantWork", names(.))|grepl("Respondent", names(.))|grepl("^DeveloperType", names(.))) 

df <- df %>%
  mutate_each(funs(strsplit(., ";")), -Respondent) 
```
```{r}
df=df %>%
  mutate(new_language=mapply(function(x, y) toString(setdiff(x, y)),
                             HaveWorkedLanguage, WantWorkLanguage),
         new_framework=mapply(function(x, y) toString(setdiff(x, y)),
                             HaveWorkedFramework, WantWorkFramework),
         new_database=mapply(function(x, y) toString(setdiff(x, y)),
                             HaveWorkedDatabase, WantWorkDatabase),
         new_platform=mapply(function(x, y) toString(setdiff(x, y)),
                             HaveWorkedPlatform, WantWorkPlatform)
         ) 
  #%>%mutate_each(funs(strsplit(., ";")), new_language:new_platform) 
```


#How many languages do devs use?
```{r}
df = df %>%
  rowwise() %>%
  mutate(num_language=length(HaveWorkedLanguage),
         num_roles=length(DeveloperType)) %>%
  ungroup()

medium_num_language = median(df$num_language)
library(scales)
df %>%
  mutate(num_language=ifelse(num_language>=10,"More than 10", as.character(num_language))) %>%
  ggplot(aes(num_language)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), width=0.5) +
  geom_text(aes(y = ((..count..)/sum(..count..)), label = scales::percent((..count..)/sum(..count..))), stat = "count", vjust = -0.25) +
  scale_y_continuous(labels=percent) +
  geom_vline(xintercept = medium_num_language, col='lightblue', linetype="dashed") +
  ggtitle("Number of languages developers use frequently") +
  theme_minimal() +
  theme(axis.title.y = element_blank(),axis.title.x = element_blank(),
  plot.title = element_text(face="bold", size=16),
  axis.text = element_text(face="bold"),
  text = element_text(family = "Helvetica"),
  plot.background = element_rect(fill = 'ghostwhite',color='white'))

#num of roles vs num of language
# df %>% 
#   group_by(num_language, num_roles) %>%
#   summarize(n=n())%>%
#   ggplot(aes(num_language, num_roles)) + 
#   geom_point(aes(size=n), alpha=0.8) + 
#   ggtitle("") 
#   theme_minimal()
```


#co-occurence networks 
```{r}
df_type <- df %>% 
  select(Respondent, DeveloperType) %>% 
  unnest() %>%
  transmute(Respondent, type = trimws(DeveloperType))%>% 
  na.omit()
```

```{r unique}
df_respondent = df_type %>%
  group_by(Respondent) %>%
  summarize(n=n())

df_type_smry = df_type %>%
  left_join(df_respondent, by = "Respondent")  %>%
  mutate(sole=ifelse(n==1,1,0))%>%
  group_by(type) %>%
  summarize(n_respondent=n(), n_sole=sum(sole))


df_type_smry %>%
  ggplot(aes(reorder(type,n_respondent))) +
  geom_bar(aes(y=n_respondent),stat="identity", alpha=0.8) +
  geom_bar(aes(y=n_sole),stat="identity",fill="gold", alpha=0.8, width=0.3) + 
  coord_flip() +
  theme_minimal() +
  ggtitle('Number of respondents') + 
  theme(axis.title.y = element_blank(),axis.title.x = element_blank(),
  plot.title = element_text(face="bold", size=16),
  axis.text = element_text(face="bold"),
  text = element_text(family = "Helvetica"),
  plot.background = element_rect(fill = 'ghostwhite',color='white'))
```


```{r}
# i='DeveloperType'
# library(lazyeval)
# df_type <- df %>% 
#   select(Respondent, i) %>% 
#     mutate_each(funs(strsplit(., ";")), -Respondent) %>%  
#   unnest_() %>%
#   mutate(type = trimws(i))%>% 
#   na.omit()
```

```{r}

co_occur_type <- sqldf("SELECT a.type a, b.type b, COUNT(*) cnt
  FROM  df_type a 
  JOIN df_type b 
  ON b.Respondent = a.Respondent AND b.type > a.type
  GROUP BY a.type, b.type") %>%
  filter(cnt>=400) #first quartile }

co_occur_g <- co_occur_type%>%
  graph_from_data_frame() 

V(co_occur_g)$size <- degree(co_occur_g, mode = 'in')
```


```{r}
draw_co_occur = function(x) {
  x%>%
  ggraph(layout = "fr") +
  geom_edge_link( aes(color = "gold", edge_alpha = cnt), show.legend = FALSE) +
  geom_node_point(color = "gold", alpha=0.8, aes(size = size)) +
  geom_node_text(color = "gold", aes(label = name), size=3, repel = TRUE) +
  theme_graph(background = 'grey20', text_colour = 'white') +
  theme(legend.position = 'None') 
}
```
```{r}
draw_co_occur(co_occur_g)
```


```{r}
framework <- df %>%
  select_if(grepl("Framework", names(.))|grepl("Respondent", names(.))|grepl("DeveloperType", names(.))) %>%
  na.omit()
```

* what's in wantedwork field that's not in haveworked field and vice versa
```{r EDA}
framework_l <- framework %>%
  select(Respondent, HaveWorkedFramework) %>%
  mutate(HaveWorkedFramework = strsplit(HaveWorkedFramework,";")) %>%
  unnest()
```


```{r}
co_occur_framework = sqldf("SELECT a.HaveWorkedFramework a, b.HaveWorkedFramework b, COUNT(*) cnt
FROM  framework_l a 
JOIN framework_l b 
ON b.Respondent = a.Respondent AND b.HaveWorkedFramework > a.HaveWorkedFramework
GROUP BY a.HaveWorkedFramework, b.HaveWorkedFramework")
```

```{r}
co_occur_framework %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = cnt), show.legend = FALSE) +
  geom_node_point(color = "purple") +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + 
  theme(legend.position = 'None')
```


```{r}
framework <- df %>%
  select_if(grepl("Framework", names(.))|grepl("Respondent", names(.))|grepl("DeveloperType", names(.))) %>%
  na.omit()
```

* what's in wantedwork field that's not in haveworked field and vice versa
```{r EDA}
language_l <- df %>%
  select(Respondent, HaveWorkedLanguage) %>%
  mutate(item = strsplit(HaveWorkedLanguage,";")) %>%
  unnest()

language_new_l <- df %>%
  select(Respondent, WantWorkLanguage) %>%
  mutate(item = strsplit(WantWorkLanguage,";")) %>%
  unnest()
```


```{r}
co_occur_language = sqldf("SELECT a.item a, b.item b, COUNT(*) cnt
FROM  language_l a 
JOIN language_l b 
ON b.Respondent = a.Respondent AND b.item > a.item
GROUP BY a.item, b.item")
```

```{r}
co_occur_language %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = cnt), show.legend = FALSE) +
  geom_node_point(color = "purple") +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme(legend.position = 'None')
```


# new skills to have
```{r}
language_l %>% 
  mutate(item = trimws(item)) %>% 
  filter(!is.na(item)) %>%
  group_by(item) %>%
  summarize(n = n()) %>%
  ggplot(aes(reorder(item, n), n)) + 
  geom_bar(stat = 'identity', color='white') + 
  coord_flip() + 
  ggtitle("") +
  theme_minimal()
  
```
```{r}
language_new_l %>% 
  mutate(item = trimws(item)) %>% 
  filter(!is.na(item)) %>%
  group_by(item) %>%
  summarize(n = n()) %>%
  ggplot(aes(reorder(item, n), n)) + 
  geom_bar(stat = 'identity', color='white') + 
  coord_flip() + 
  ggtitle("") +
  theme_minimal()
```
##animating the difference
```{r}
library(gganimate)
library(data.table)
library(tweenr)
my.list <- list(language_l, language_new_l)
language_l_future = language_l %>%left_join(language_new_l, by='Respondent')
tf <- tween_states(my.list, tweenlength= 2, statelength=3, ease=rep('cubic-in-out',51),nframes=100)
dtf <- data.table(tf)
p <- ggplot(aes( ,frame=.frame))
gganimate(p, “ex2_tween.gif")
```

# New languages/frameworks/platforms/databases devs want to work on (that they current don't work on)

```{r}
df_new_language <- df %>% 
  select(Respondent, new_language) %>% 
  mutate(new_language = strsplit(as.character(new_language),",")) %>% 
  unnest() %>%
  transmute(Respondent, type = trimws(new_language))%>% 
  na.omit()
```

```{r}
co_occur_language <- sqldf("SELECT a.type a, b.type b, COUNT(*) cnt
  FROM df_new_language a 
  JOIN df_new_language  b 
  ON b.Respondent = a.Respondent AND b.type > a.type
  GROUP BY a.type, b.type") %>%
  filter(cnt>=24) #first quartile }

co_occur_g <- co_occur_language%>%
  graph_from_data_frame() 
V(co_occur_g)$size <- degree(co_occur_g, mode = 'in')

draw_co_occur(co_occur_g)
```

```{r}
df_new_platform <- df %>% 
  select(Respondent, new_platform) %>% 
  mutate(new_platform=strsplit(new_platform,",")) %>% 
  unnest() %>%
  transmute(Respondent, type = trimws(new_platform))%>% 
  na.omit()
```
```{r}
co_occur_platform <- sqldf("SELECT a.type a, b.type b, COUNT(*) cnt
  FROM df_new_platform a 
  JOIN df_new_platform  b 
  ON b.Respondent = a.Respondent AND b.type > a.type
  GROUP BY a.type, b.type") %>%
  filter(cnt>=24) #first quartile }

co_occur_g <- co_occur_platform%>%
  graph_from_data_frame() 
V(co_occur_g)$size <- degree(co_occur_g, mode = 'in')

draw_co_occur(co_occur_g)
```

```{r}
df_new_framework <- df %>% 
  select(Respondent, new_framework) %>% 
  mutate(new_framework=strsplit(new_framework,",")) %>% 
  unnest() %>%
  transmute(Respondent, type = trimws(new_framework))%>% 
  na.omit()
```
```{r}
co_occur_framework <- sqldf("SELECT a.type a, b.type b, COUNT(*) cnt
  FROM df_new_framework a 
  JOIN df_new_framework  b 
  ON b.Respondent = a.Respondent AND b.type > a.type
  GROUP BY a.type, b.type") %>%
  filter(cnt>=24) #first quartile }

co_occur_g <- co_occur_framework%>%
  graph_from_data_frame() 
V(co_occur_g)$size <- degree(co_occur_g, mode = 'in')

draw_co_occur(co_occur_g)
```

```{r}
df_new_database <- df %>% 
  select(Respondent, new_database) %>% 
  mutate(new_database=strsplit(new_database,",")) %>% 
  unnest() %>%
  transmute(Respondent, type = trimws(new_database))%>% 
  na.omit()
```
```{r}
co_occur_database <- sqldf("SELECT a.type a, b.type b, COUNT(*) cnt
  FROM df_new_database a 
  JOIN df_new_database  b 
  ON b.Respondent = a.Respondent AND b.type > a.type
  GROUP BY a.type, b.type") %>%
  filter(cnt>=24) #first quartile }

co_occur_g <- co_occur_database%>%
  graph_from_data_frame() 
V(co_occur_g)$size <- degree(co_occur_g, mode = 'in')

draw_co_occur(co_occur_g)
```