---
title: "Cuisine culture"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=F, warning=F, echo=F)
#chart
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(RColorBrewer)
library(gridExtra) #contain hex to RGB conversion
library(ggrepel)
library(wesanderson)
#sql
library(sqldf)
#text
library(tidytext)
#library(RJSONIO) 
#graph
library(ggnetwork)
library(igraph)
library(ggraph)
library(threejs)
#plotly
library(plotly)
#theme
my_theme <- function(base_size = 12, base_family = "Helvetica"){
    theme_minimal() +
    theme(axis.title.y = element_blank(),axis.title.x = element_blank(),
    plot.title = element_text(face="bold", size=16),
    axis.text.x = element_blank(),
    plot.background = element_rect(fill = 'ghostwhite',color='white'),
    legend.position = 'None', legend.title = element_blank())
}

col <- wes_palette("Darjeeling1", 20, type = "continuous")
#col<-rep('#959F24',20)
```

## Load data


```{r}
# data source: the data contains 39774 recipes from yummly 

#key cleaning steps
#1. google refine to cluster similar names
#2. remove words describing physical state of the ingredients such as dried/fresh/minced
df <- read.csv("~/git_repo/opendata_viz/cuisine_culture/recipe-ingredients-dataset/cleaned_ingredients.csv", stringsAsFactors=FALSE) %>%
  mutate(Cuisine=toupper(gsub('_',' ',Cuisine))) %>%
  mutate(Ingredients = trimws(gsub('crushed|crumbles|ground|minced|chopped|sliced|dried|fresh|frozen|superfine|unsalted|grated|shredded|large|granulated|unsweetened|unsalted|cloves','',Ingredients))) %>%
  #turn different forms of ingredient into one
  mutate(Ingredients = ifelse(grepl('tomato',Ingredients),'tomato',Ingredients))%>%
  
  mutate(Cuisine=factor(Cuisine, levels=c("ITALIAN","FRENCH", "BRITISH","IRISH",
                  "CHINESE","KOREAN", "JAPANESE","THAI","VIETNAMESE","FILIPINO",
                  "SOUTHERN US", "MEXICAN", "INDIAN",      
                 "CAJUN CREOLE","GREEK", "MOROCCAN", "SPANISH",
                  "RUSSIAN", "JAMAICAN", "BRAZILIAN" ))) 

```





# Frequency
```{r}
#ingredients that appear in at least 10 recipes
distinct_ingredients<-df %>%
  count(Ingredients, Cuisine, sort=T) %>%
  filter(n > 10) %>%
  bind_tf_idf(Ingredients, Cuisine, n) %>%
  arrange(desc(tf_idf, n)) 

top_distinct_ingredients <- distinct_ingredients%>% 
  group_by(Cuisine) %>%
  top_n(5, tf_idf) 

write.csv(top_distinct_ingredients,'distinct_ingredients.csv')
```

most distinct 
```{r facetplot}
top_distinct_ingredients %>% 
  ggplot(aes(reorder(Ingredients, tf_idf), tf_idf, fill=Cuisine)) + 
  geom_bar(stat="identity", aes(label=Ingredients)) +
  facet_wrap(~Cuisine, scales='free', ncol=4) +
  theme_minimal() + coord_flip() + my_theme() + scale_fill_manual(values=col) + 
  labs(title = 'Signature Ingredients by Cuisine', caption = 'Ranked by uniqueness', source='Yummly')
  
```

## Ingredient frequency count

```{r}
#filter for more than 1% in any category
ingredient <- df %>% count(Cuisine, Ingredients, sort=T) %>%
  filter(!Ingredients %in% c('salt','pepper','water','oil')) %>%
  bind_tf_idf(Ingredients, Cuisine, n) %>%
  group_by(Cuisine) %>% 
  mutate(pct=n/sum(n)) %>% 
  filter(pct>=0.008) %>% 
  ungroup() %>%
  mutate(Cuisine=toTitleCase(tolower(as.character(Cuisine))))

#write.csv(ingredient,'ingredient_original.csv')

i<- df %>% count(Ingredients, sort=T) 
```

co-occuring ingredients globally
```{r sql}
co_occur = sqldf("SELECT a.Ingredients a, b.Ingredients b, COUNT(*) cnt
  FROM  df a 
  JOIN df b 
  ON b.doc_id = a.doc_id AND b.Ingredients > a.Ingredients
  WHERE b.Ingredients NOT IN ('salt','pepper','water') 
    AND a.Ingredients NOT IN ('salt','pepper','water')
  GROUP BY a.Ingredients, b.Ingredients")
```

# obtain degree centrality for all ingredients
```{r}
g.complete <- co_occur %>% 
  graph_from_data_frame() 

versality <- as.data.frame(degree(g)) %>% 
  rownames_to_column(var = "Ingredients") %>%
  rename(degree = `degree(g)`) %>% na.omit()
write.csv(versality,'versality.csv')
```

```{r}
ingredient.w <- ingredient %>%
  select(Cuisine, Ingredients, tf_idf) %>%
  spread(Cuisine, tf_idf) %>% 
  replace(is.na(.), 0) %>% 
  left_join(i) %>%
  left_join(versality)

write.csv(ingredient.w,'ingredient.csv')
```

most frequent
```{r}
df %>% 
  filter(!Ingredients %in% c('salt','pepper','water')) %>%
  count(Cuisine, Ingredients) %>%
  group_by(Cuisine) %>% top_n(5) %>%
  ggplot(aes(reorder(Ingredients, n), n, fill=Cuisine)) + 
  geom_bar(stat="identity", aes(label=Ingredients)) +
  facet_wrap(~Cuisine, scales='free', ncol=4) +
  theme_minimal() + coord_flip() + my_theme() + scale_fill_manual(values=col) + 
  labs(title = 'Frequent Ingredients by Cuisine', caption = 'Ranked by frequency', source='Yummly')
  

```




```{r}
g <- co_occur %>% 
  filter(cnt>1000)  %>%
  graph_from_data_frame() 

V(g)$Popularity <- degree(g)

g %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = cnt), show.legend = FALSE) +
  geom_node_point(color = "darkgreen") +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() + 
  theme(legend.position = 'None') 
```

Asian soy sauce connected western flour-based meal and olive oil based meals.

# Quitessential ingredients

```{r}
co_occur_cuisine = sqldf("SELECT a.Cuisine, a.Ingredients a, b.Ingredients b, COUNT(*) cnt
  FROM  df a 
  JOIN df b 
  ON b.doc_id = a.doc_id AND b.Ingredients > a.Ingredients
  WHERE b.Ingredients NOT IN ('salt','water') AND a.Ingredients NOT IN ('salt','water')
  GROUP BY a.Cuisine,a.Ingredients, b.Ingredients")
```


```{r}
co_occur_select <- co_occur_cuisine %>% 
  arrange(-cnt) %>% 
  group_by(Cuisine) %>%
  top_n(10) %>% select(-Cuisine,everything())
```

```{r}
cuisine_network = function(i) {
  cuisine <- co_occur_select %>%
  filter(Cuisine==list_cuisine[i]) %>% 
  graph_from_data_frame() 
  
 
  
  V(cuisine)$Popularity <- igraph::degree(cuisine, mode='all')
  
  (clu <- igraph::components(cuisine))
  gMax <- induced_subgraph(cuisine, V(cuisine)[clu$membership == which.max(clu$csize)])
  
  gMax%>%
  ggraph(layout = 'fr') +
  geom_edge_link(aes(edge_alpha = cnt), edge_colour = 'black', show.legend = FALSE) +
  geom_node_point(color = col[i], aes(size=Popularity, alpha=scale(log(Popularity)))) +
  geom_node_text(color = col[i],aes(label = name), repel = TRUE) +
  ggtitle(list_cuisine[i]) +
  theme_void() + 
  theme(legend.position = 'None', 
        plot.title = element_text(face="bold", size=16, color=col[i]),
        plot.background = element_rect(fill = 'ghostwhite',color='grey'),
        plot.margin = margin(5, 5, 5, 5, "pt")) 
} 

```

```{r}
myplots <- list()
png('ingredient pairing.png',height=1000)

list_cuisine <- unique(df$Cuisine)
  #unique(co_occur_select$Cuisine)

for (i in 1:20) {
  cuisine_network(i) -> myplots[[i]]
}

do.call("grid.arrange", c(myplots, ncol=2))
dev.off()
```

```{r}
myplots <- list()
for (i in 1:2) {
  cuisine_network(i) -> myplots[[i]]
}

do.call("grid.arrange", c(myplots, ncol=2))
```

Focus on a few ingredients such as soy sauce.

```{r}
g <- graph_from_data_frame(co_occur)
#subset graph

plot_subgraph <- function(g, x) {
  g.sub=make_ego_graph(g, 1, nodes = x, mode = c("all"))[[1]] #make a graph only with nodes connected to vertex 184 directly or indirectly
  
  #get distance of all the nodes from node 184
  dists <- distances(g.sub, x)
  
  colors <- c("black", "red", "orange", "blue", "dodgerblue", "cyan")
  V(g.sub)$color <- colors[dists+1] #because lists will start from 0 and ends at diameter, and we want to color point 184 too.
  
  # Visualize the network based on geodesic distance from vertex 184 (patient zero).
  plot(g.sub, 
       #vertex.label=NA,
       edge.color = 'grey',
       vertex.size = 7,
       vertex.color = 'brown',
       edge.arrow.size = .05,
       main = ""
       )
}
```

```{r}
g.filtered=graph_from_data_frame(filter(co_occur,cnt>200))
plot_subgraph(g.filtered, 'pasta')
```


```{r}
c = unique(co_occur_cuisine$Cuisine)


soy = co_occur_cuisine %>% filter(a=='soy sauce'|b=='soy sauce') %>% filter(cnt>=50) %>%select(-cnt)

plot(graph_from_data_frame(soy),
     vertex.shape=c("circle","square"), 
     edge.arrow.size=0.1, vertex.label.family='Helvetica',
     vertex.label.color='black',
     vertex.label.cex = 0.7)

```

#most used ingredients
```{r}
common_ingredients <- df %>%
  filter(!grepl('salt|pepper',Ingredients))%>%
  count(Ingredients, sort=T) %>%
  head(100)
```

# recommendation tree
```{r}
x=df%>%filter(Ingredients=='chicken')
```

to do:

make it bipartite https://www.r-bloggers.com/collapsing-a-bipartite-co-occurrence-network/
which countries are most similar
which ingredients connects cultures

