---
title: "Cuisine culture"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = F, warning = F, echo = F)
# chart
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(RColorBrewer)
library(gridExtra) # contain hex to RGB conversion
library(ggrepel)
library(wesanderson)
# sql
library(sqldf)
# text
library(tidytext)
library(widyr)
# library(RJSONIO)
# graph
library(ggnetwork)
library(igraph)
library(ggraph)
# plotly
library(plotly)
# theme
my_theme <- function(base_size = 12, base_family = "Helvetica") {
  theme_minimal() +
    theme(
      axis.title.y = element_blank(), axis.title.x = element_blank(),
      plot.title = element_text(face = "bold", size = 16),
      axis.text.x = element_blank(),
      plot.background = element_rect(fill = "ghostwhite", color = "white"),
      legend.position = "None", legend.title = element_blank()
    )
}

#col <- wes_palette("Darjeeling1", 20, type = "continuous")
# col<-rep('#959F24',20)
col <- viridis(20, option='B', begin=0.15,end=0.85)
```

## Load data


```{r}
# data source: the data contains 39774 recipes from yummly

# key cleaning steps
# 1. google refine to cluster similar names
# 2. remove words describing physical state of the ingredients such as dried/fresh/minced
df <- read.csv("~/git_repo/opendata_viz/cuisine_culture/recipe-ingredients-dataset/cleaned_ingredients.csv", stringsAsFactors = FALSE) %>%
  mutate(Cuisine = toupper(gsub("_", " ", Cuisine))) %>%
  mutate(Ingredients = trimws(gsub("crushed|crumbles|ground|minced|chopped|sliced|dried|fresh|frozen|superfine|unsalted|grated|shredded|large|granulated|unsweetened|unsalted|cloves|extra-virgin|seeds", "", Ingredients))) %>%
  # turn different forms of ingredient into one
  mutate(Ingredients = ifelse(grepl("tomato", Ingredients), "tomato", Ingredients)) %>%
  mutate(Cuisine = factor(Cuisine, levels = c(
    "ITALIAN", "FRENCH", "BRITISH", "IRISH",
    "CHINESE", "KOREAN", "JAPANESE", "THAI", "VIETNAMESE", "FILIPINO",
    "SOUTHERN US", "MEXICAN", "INDIAN",
    "CAJUN CREOLE", "GREEK", "MOROCCAN", "SPANISH",
    "RUSSIAN", "JAMAICAN", "BRAZILIAN"
  )))
```

How many pastry/baking recipe
```{r}
ttl <- n_distinct(df$doc_id)
pastry <- df %>% filter(grepl("baking|rising|pastry|dough", Ingredients)) %>% select(doc_id) %>% left_join(df)
n_distinct(pastry %>% select(doc_id))
n_distinct(pastry %>% select(doc_id)) / ttl

# containing flour doesn't necessarily mean pastry, it could be fried food or taco etc
```




# Frequency
```{r}
# ingredients that appear in at least 10 recipes
distinct_ingredients <- df %>%
  count(Ingredients, Cuisine, sort = T) %>%
  filter(n > 10) %>%
  bind_tf_idf(Ingredients, Cuisine, n) %>%
  arrange(desc(tf_idf, n))

top_distinct_ingredients <- distinct_ingredients %>%
  group_by(Cuisine) %>%
  top_n(5, tf_idf)

# write.csv(top_distinct_ingredients,'distinct_ingredients.csv')
```

most distinct 
```{r facetplot}
library(viridis)
top_distinct_ingredients %>%
  ggplot(aes(reorder(Ingredients, tf_idf), tf_idf,fill=Cuisine)) +
  geom_bar(stat = "identity", aes(label = Ingredients),width=0.3) +
  facet_wrap(~Cuisine, scales = "free", ncol = 4) +
  theme_minimal() + coord_flip() + my_theme() + 
  labs(title = "Signature Ingredients by Cuisine", caption = "Ranked by uniqueness", source = "Yummly") + 
  scale_fill_viridis(discrete=T, begin=0.2,end=0.8,option='B')
```

## Ingredient frequency count

```{r}
# filter for more than 1% in any category
ingredient <- df %>%
  count(Cuisine, Ingredients, sort = T) %>%
  filter(!Ingredients %in% c("salt", "pepper", "water", "oil")) %>%
  group_by(Cuisine) %>%
  filter(n >= sum(n) * 0.008) %>%
  ungroup() %>%
  bind_tf_idf(Ingredients, Cuisine, n) %>%
  mutate(Cuisine = tools::toTitleCase(tolower(as.character(Cuisine))))

# write.csv(ingredient,'ingredient_original.csv')

i <- df %>% count(Ingredients, sort = T)
```


# network

co-occuring ingredients globally
```{r sql}
co_occur <- sqldf("SELECT a.Ingredients a, b.Ingredients b, COUNT(*) cnt
  FROM  df a 
  JOIN df b 
  ON b.doc_id = a.doc_id AND b.Ingredients > a.Ingredients
  WHERE b.Ingredients NOT IN ('salt','pepper','water') 
    AND a.Ingredients NOT IN ('salt','pepper','water')
  GROUP BY a.Ingredients, b.Ingredients")
```



```{r}
g <- co_occur %>%
  filter(cnt > 1000) %>%
  graph_from_data_frame()

V(g)$Popularity <- degree(g)

g %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = cnt), show.legend = FALSE) +
  geom_node_point(color = "darkgreen") +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void() +
  theme(legend.position = "None")
```

obtain degree centrality for all ingredients
```{r}
g.complete <- co_occur %>%
  graph_from_data_frame()

versality <- as.data.frame(degree(g)) %>%
  rownames_to_column(var = "Ingredients") %>%
  rename(degree = `degree(g)`) %>%
  na.omit()
write.csv(versality, "versality.csv")
```

```{r}
#for tableau input
ingredient.w <- ingredient %>%
  select(Cuisine, Ingredients, tf_idf) %>%
  spread(Cuisine, tf_idf) %>%
  replace(is.na(.), 0) %>%
  left_join(i) %>%
  left_join(versality)

# write.csv(ingredient.w,'ingredient.csv')
```

## most frequent ingredients by cuisine plot
```{r}
df %>%
  filter(!Ingredients %in% c("salt", "pepper", "water")) %>%
  count(Cuisine, Ingredients) %>%
  group_by(Cuisine) %>%
  top_n(5) %>%
  ggplot(aes(reorder(Ingredients, n), n)) +
  geom_bar(stat = "identity", aes(label = Ingredients), fill="#96017C",width=0.3) +
  facet_wrap(~Cuisine, scales = "free", ncol = 4) +
  theme_minimal() + coord_flip() + my_theme() + 
  labs(title = "Frequent Ingredients by Cuisine", caption = "Ranked by frequency", source = "Yummly")
```



# Quitessential ingredients

```{r}
co_occur_cuisine <- sqldf("SELECT a.Cuisine, a.Ingredients a, b.Ingredients b, COUNT(*) cnt
  FROM  df a 
  JOIN df b 
  ON b.doc_id = a.doc_id AND b.Ingredients > a.Ingredients
  WHERE b.Ingredients NOT IN ('salt','water') AND a.Ingredients NOT IN ('salt','water')
  GROUP BY a.Cuisine,a.Ingredients, b.Ingredients")
```


```{r}
co_occur_select <- co_occur_cuisine %>%
  arrange(-cnt) %>%
  group_by(Cuisine) %>%
  top_n(10) %>%
  select(-Cuisine, everything())
```

```{r}
cuisine_network <- function(i) {
  cuisine <- co_occur_select %>%
    filter(Cuisine == list_cuisine[i]) %>% 
    graph_from_data_frame()



  V(cuisine)$Popularity <- igraph::degree(cuisine, mode = "all")

  (clu <- igraph::components(cuisine))
  gMax <- induced_subgraph(cuisine, V(cuisine)[clu$membership == which.max(clu$csize)])

  gMax %>%
    ggraph(layout = "linear") +
    geom_edge_arc(aes(edge_alpha = cnt), edge_colour = col[i], show.legend = FALSE) +
    geom_node_point(color = col[i], aes(size = Popularity, alpha = scale(log(Popularity)))) +
    geom_node_text(color = col[i], aes(label = name), repel = TRUE,size=4) +
    ggtitle(list_cuisine[i]) +
    theme_void() +
    theme(
      legend.position = "None",
      plot.title = element_text(face = "bold", size = 16, color = col[i]),
      plot.background = element_rect(fill = "ghostwhite", color = "grey"),
      plot.margin = margin(5, 5, 5, 5, "pt")
    )
}
```

```{r}

png("ingredient pairing.png",  width=600)
myplots <- list()
list_cuisine <- c(
    "ITALIAN", "FRENCH", "BRITISH", "IRISH",
    "CHINESE", "KOREAN", "JAPANESE", "THAI", "VIETNAMESE", "FILIPINO",
    "SOUTHERN US", "MEXICAN", "INDIAN",
    "CAJUN CREOLE", "GREEK", "MOROCCAN", "SPANISH",
    "RUSSIAN", "JAMAICAN", "BRAZILIAN"
  )
# unique(co_occur_select$Cuisine)

for (i in 1:20) {
  cuisine_network(i) -> myplots[[i]]
}

do.call("grid.arrange", c(myplots, ncol = 4))
dev.off()

```


Focus on a few ingredients such as soy sauce.

```{r}
g <- graph_from_data_frame(co_occur)
# subset graph

plot_subgraph <- function(g, x) {
  g.sub <- make_ego_graph(g, 1, nodes = x, mode = c("all"))[[1]] # make a graph only with nodes connected to vertex 184 directly or indirectly

  # get distance of all the nodes from node 184
  dists <- distances(g.sub, x)

  colors <- c("black", "red", "orange", "blue", "dodgerblue", "cyan")
  V(g.sub)$color <- colors[dists + 1] # because lists will start from 0 and ends at diameter, and we want to color point 184 too.

  # Visualize the network based on geodesic distance from vertex 184 (patient zero).
  plot(g.sub,
    # vertex.label=NA,
    edge.color = "grey",
    vertex.size = 7,
    vertex.color = "brown",
    edge.arrow.size = .05,
    main = ""
  )
}
```

```{r}
g.filtered <- graph_from_data_frame(filter(co_occur, cnt > 200))
plot_subgraph(g.filtered, "pasta")
```


```{r}
c <- unique(co_occur_cuisine$Cuisine)


soy <- co_occur_cuisine %>% filter(a == "soy sauce" | b == "soy sauce") %>% filter(cnt >= 50) %>% select(-cnt)

plot(graph_from_data_frame(soy),
  vertex.shape = c("circle", "square"),
  edge.arrow.size = 0.1, vertex.label.family = "Helvetica",
  vertex.label.color = "black",
  vertex.label.cex = 0.7
)
```

#most universal ingredients

Some regional ingredients show up in other cuisine likely due to migration and fusion cuision, such as parmesan cheese in what's labeled as Chinese recipe and soy sauce in what's labeled as Southern US.

```{r}
common_ingredients <- df %>%
  filter(!grepl("salt|pepper", Ingredients)) %>%
  count(Ingredients, sort = T) %>%
  head(100)

filter_for <- function(x) {
  df %>% filter(Ingredients == x) %>% group_by(Cuisine) %>% tally()
}
filter_for("parmesan cheese")
```

## Find similar cuisines

```{r}
library("REdaS")
# radian to degree conversion
cuisine_similiarity <- df %>%
  count(Ingredients, Cuisine, sort = T) %>%
  pairwise_similarity(Cuisine, Ingredients, n) %>%
  arrange(desc(similarity)) %>%
  mutate(angle = rad2deg(acos(similarity))) %>%
  replace(is.na(.), 0)

write.csv(cuisine_similiarity, "cuisine_similiarity.csv")

cuisine_similiarity %>%
  ggplot(aes(item1, item2)) + geom_tile(aes(fill = similarity)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_fill_gradient(low = "white", high = "blue")
```

when user has celery and egg

```{r}
df %>%
  group_by(doc_id, Cuisine) %>% 
  summarize(allingredients = paste(Ingredients, collapse=' ')) %>% 
  filter(grepl("eggs", allingredients)&grepl("celery", allingredients)&grepl("chicken", allingredients)) %>%
  group_by(Cuisine) %>%
  summarize(n = n_distinct(doc_id)) %>%
  ggplot(aes(Cuisine, n)) +
  geom_segment(aes(x = Cuisine, y = 0, xend = Cuisine, yend = n)) +
  geom_text(aes(label = ifelse(n > 1000, df$Cuisine, ""))) +
  geom_point(aes(col = Cuisine, alpha = 0.6)) + coord_polar() +
  theme_void() + theme(legend.position = "None")
```

to do:
predict cuisine

