+---
title: "Oscars"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE, warning=FALSE}
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(dplyr)
library(reshape2)
library(tidyr)
library(formattable)
library(RColorBrewer)
library(gridExtra)
library(plotly)
library(viridis)
library(ggthemes)
library(png)
library(networkD3)
#data from https://www.kaggle.com/theacademy/academy-awards
oscars <- read_csv("oscars.csv")

```

```{r}
# top10 <- oscars %>% 
#   filter(Winner == 1, !is.na(Film)) %>% 
#   count(Film, sort=T) %>% head(10)
# oscarstop10 <- oscars %>%
#   filter(Film%in%top10$Film)
# write.csv(oscarstop10 , 'oscarstop10 .csv')
```
Top studio by nomination
```{r}
topstudio = oscars%>%
  filter(grepl('Product|Short Subject', Award)) %>% 
  filter(!grepl(', Producer',Film))%>% 
  count(Film, sort=T) %>% head(7)
oscarstop10studio <- oscars %>%
  filter(Film%in% c(topstudio$Film,'Walt Disney, Producer'))
write.csv(oscarstop10studio, 'oscarstop10studio.csv')
```
Top studio by winning
```{r}
oscarstop10studiowin <- oscars %>% 
  filter(Film%in% c(topstudio$Film,'Walt Disney','20th Century-Fox')) %>% 
  filter(Winner==1) 
write.csv(oscarstop10studiowin, 'oscarstop10studiowin.csv')
```

#Top in acting/directing
```{r}

winner <- oscars %>% 
  filter(Winner == 1, !is.na(Film)) 

n_film = winner %>%
  count(Film, sort=T) %>% rename(n_film=n)
n_entity = winner %>%
  count(Name, sort=T) %>% rename(n_entity=n)

winner = winner %>% 
  filter(grepl('actor|actress|director', Award, ignore.case=TRUE))   %>% 
  left_join(n_film) %>% 
  left_join(n_entity) %>% 
  filter(n_entity>1)

write.csv(winner, 'winner.csv')
```

#all category most awards
```{r}
overall = oscars %>% 
  filter(Winner == 1, !is.na(Film)) %>% 
  left_join(n_film) %>% 
  left_join(n_entity) %>% 
  filter(n_entity>3|n_film>3)
write.csv(overall, 'overall.csv')
```

First I filter for those actors and actress with winning history both 1 and NA


```{r}
winner_at_last <- oscars %>% 
  filter(grepl("Actor",Award)|grepl("Actress", Award)) %>% 
  select(Name, Winner, Year, Award)%>%
  group_by(Name, Winner, Award) %>%
  summarize(count=n())%>%
  spread(Winner, count)%>%
  na.omit() %>%
  melt()

```

Then I look at how many years have passed in between their two consecutive nominations


```{r}
df <- oscars %>%
  filter(Name %in% winner_at_last$Name) %>% 
  group_by(Name) %>%
  arrange(Name, Ceremony) %>%
  mutate(gap = Ceremony - lag(Ceremony, 1)) %>%
  mutate(gap = ifelse(is.na(gap),0,gap)) %>%
  mutate(gap_sum = cumsum(gap))
```

Then I divided them into Actor groups and Actress groups. Each were eligible to win Lead actor/actress, supporting actor/actress, honorary award, special award and humanitarian award.

```{r}
Actor <- winner_at_last %>% filter(grepl("Actor",Award)) %>% distinct(Name)
Actress <- winner_at_last %>% filter(grepl("Actress",Award)) %>% distinct(Name)
```

```{r, fig.width=5, fig.height=5}
require(gridExtra)
p1= df %>% 
  filter(Name %in% Actor$Name) %>%
  ggplot(aes(Name, gap_sum))+
  geom_point(aes(col=factor(Winner), shape=Award))+
  scale_fill_manual(values = c("red","grey"))+
  coord_flip()+
  labs(x = "Actors")+
  theme_minimal() +
  guides(color=FALSE)+
  theme(legend.position="bottom")

p2=df %>% filter(Name %in% Actress$Name) %>%
  ggplot(aes(Name, gap_sum)) +
  geom_point(aes(col=factor(Winner), shape=factor(Award)))+
  scale_fill_manual(values = c("red","grey"))+
  coord_flip()+
  labs(x = "Actresses")+
  theme_minimal()+
  theme(legend.position="none") 

grid.arrange(p1, p2, ncol=2)
```
```{r}
df %>% 
  filter(Name %in% Actor$Name) %>%
  ggplot(aes(Name, gap_sum))+
  geom_point(aes(col=factor(Winner), shape=Award))+
  scale_fill_manual(values = c("red","grey"))+
  coord_flip()+
  labs(x = "Actors")+
  theme_minimal() +
  guides(color=FALSE)+
  theme(legend.position="bottom") + coord_polar() + 
  theme(axis.title.y = element_blank(),axis.title.x = element_blank(),
  plot.title = element_text(face="bold", size=16),
  axis.text = element_blank(),
  plot.background = element_rect(fill = 'black',color='white')) +
  labs(title = "",
  subtitle = "")
```


Then I look at who have been nominated the most times: none other than Meryl Streep!

```{r}
df %>% count(Name, sort=T) %>% head() %>% formattable(align="l")
```


```{r winmost}
df %>% filter(Winner == 1)%>%
  count(Name, sort=T) %>% head() %>% formattable(align="l")
```


Who have won the most times? Katharine Hepburn with 4 statuettes

```{r}
df %>% filter(Winner==1) %>% count(Name, sort=T) %>% head() %>% formattable(align="l")
```

Who are the ones recognized by the ceremony throughout decades of their careers?

```{r}
df %>% arrange(-gap_sum) %>% head() %>% formattable(align="l")
```

Who waited the longest between first nomination and actually winning for the 1st time?
It's been 38 years before Alan Arkin and Jack Palance first won Actor in a supporting role.

```{r}
waittime <- df %>% mutate(Year = as.numeric(Year))%>%
  filter(!is.na(Winner)) %>%
  group_by(Name) %>%
  filter(!duplicated(Winner==1)) %>% 
  arrange(desc(gap_sum)) %>%
  ungroup() %>%
  mutate(first_nominated=Year-gap_sum, Name = reorder(Name, gap_sum)) %>%
  head(10) 
```

```{r}
waittime %>% mutate() %>% 
    ggplot(aes(Name)) +
    geom_linerange(aes(ymin = first_nominated, ymax = Year)) + 
    geom_point(aes(y =first_nominated), color="darkorchid3", size=2) +
    geom_point(aes(y = Year), color="yellowgreen",size=2.5, shape=8) + 
  geom_text(aes(y=Year+3, label = gap_sum)) +
  coord_flip()+
    theme(legend.position = "None",
          axis.title.x=element_blank(),
      panel.grid.major.x = element_blank()) +
  scale_y_continuous(breaks = seq(1950,2015,10)) +
  ggtitle("Years From First Nominated to Finally winning") +
   theme_tufte()
```

#network
```{r}

```


