```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=F, warning=F)
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(RColorBrewer)
library(plotly) #contain hex to RGB conversion
library(jsonlite)
library(stringr)
#plot
library(plotly)
#theme
my_theme <- function(base_size = 12, base_family = "Helvetica"){
    theme_minimal() +
    theme(axis.title.y = element_blank(),axis.title.x = element_blank(),
    plot.title = element_text(face="bold", size=16),
    axis.text = element_text(face="bold"),
    plot.background = element_rect(fill = 'ghostwhite',color='white'),
    legend.position = 'None', legend.title = element_blank())
}

```

Based on refreshed data on kaggle (till 2017)

```{r}
ted <- read_csv("~/git_repo/opendata_viz/TED/ted_new.csv")
rating <- ted %>%
  mutate(ratings=str_replace_all(ratings, "\'", "\""))%>%
  select(ratings) %>% 
  as.data.frame()
```

## json
parse out json column that contains 14 ratings (beautiful, jaw-dropping, etc)

```{r}
parse = function(x) {
  fromJSON(x) %>% select(name, count)%>% spread(name, count)
}
```


```{r}
list_rating <- lapply(rating$ratings, parse)
rating_parsed <- bind_rows(list_rating)
```

## normalize
Ken Robinson's talk is among the most 'long-winded', only because it has highest viewership. normalization is needed here. Each talk would have highest attribute to 1

```{r}
range01 <- function(x){(max(x)-min(x))}
rating_parsed$max_rating <- do.call(pmax, rating_parsed)
ted_scaled <- rating_parsed %>%
   mutate_all(funs(./max_rating))

ted_combine <- ted %>%
  select(title, speaker_occupation, duration) %>%
  cbind(ted_scaled)

```

## simplify occupation field
```{r}
patternreplace = function(x, patterns, replacements = patterns, fill = NA, ...)
  {
stopifnot(length(patterns) == length(replacements))
ans = rep_len(as.character(fill), length(x))    
empty = seq_along(x)

for(i in seq_along(patterns)) {
greps = grepl(patterns[[i]], x[empty], ... , ignore.case = T)
ans[empty[greps]] = replacements[[i]]  
empty = empty[!greps]
}
return(ans)
}
```

## parsing occupation 
```{r}
top_occupation <- ted_combine %>%
  count(speaker_occupation, sort=T) %>%
  head(30)

from = c(top_occupation$speaker_occupation,'Engineer','Futurist','Mathematician')
to = c("Writer", "Artist/Designer","Artist/Designer","Journalist",
  "Entrepreneur","Architect","Inventor","Psychologist","Photographer","Filmmaker",
  "Scientist/Technologist","Writer","Economist","Educator","Scientist/Technologist",
  "Scientist/Technologist","Philosopher","Scientist/Technologist","Scientist/Technologist",
  "Musician", "Activist","Visionary","Scientist/Technologist", "Astronomer", "Behavioral economist","Artist/Designer", "Historian","Scientist/Technologist","Philanthropist","Writer",
  "Scientist/Technologist","Futurist","Scientist/Technologist"
)

ted_combine <- ted_combine %>%
  mutate(occupation = patternreplace(speaker_occupation, from, to)) %>%
  mutate(occupation = ifelse(is.na(occupation),'others',occupation),
         occupation_code = as.numeric(as.factor(occupation)))
```

```{r}
ted_combine %>%
  count(occupation, sort=T) %>%
  head(20)
write.csv(ted_combine, 'ted_combine.csv')
```

## brushing parcoord in plot.ly by attribute

```{r}
ted_combine %>%
  plot_ly(type = 'parcoords',
          line = list(color = '#ff6f69'),
          dimensions = list(
            list(label = 'Beautiful', values = ~Beautiful),
            list(label = 'Inspiring', values = ~Inspiring),
            list(label = 'Fascinating', values = ~Fascinating),
            list(label = 'Courageous', values = ~Courageous),
            list(label = 'Funny', values = ~Funny),
            list(label = 'Informative', values = ~Informative),
            list(constraintrange = c(0.9,1),label = 'Ingenious', values = ~Ingenious),
            list(label = 'Persuasive', values = ~Persuasive),
            list(label = 'Obnoxious', values = ~Obnoxious),
            list(label = 'Unconvincing', values = ~Unconvincing),
            list(label = 'Confusing', values = ~Confusing),
            list(label = 'Jaw-dropping', values = ~'Jaw-dropping'),
            list(label = 'Longwinded', values = ~Longwinded)
            )
          )
```

Showing attribute by speaker occupation is theoretically possible on discrete palette, but a bit sense here given the number of talks and diversity of speakers
```{r}
#in plotly the line color encoding has to be numerics, not factors
ted_combine %>%
plot_ly(type = 'parcoords',
          #line = list(color = ~occupation_code,
          #            colorscale = list(c(1,'red'),c(2,'green'),c(3,'blue'))),
           line = list(color = ~occupation_code,
                      colorscale = 'jet'
                     ),
          dimensions = list(
            list(constraintrange = c(0.9,1),label = 'Beautiful', values = ~Beautiful),
            list(label = 'Inspiring', values = ~Inspiring),
            list(label = 'Fascinating', values = ~Fascinating),
            list(label = 'Courageous', values = ~Courageous),
            list(label = 'Funny', values = ~Funny),
            list(label = 'Informative', values = ~Informative),
            list(label = 'Ingenious', values = ~Ingenious),
            list(label = 'Persuasive', values = ~Persuasive),
            list(label = 'Obnoxious', values = ~Obnoxious),
            list(label = 'Unconvincing', values = ~Unconvincing),
            list(label = 'Confusing', values = ~Confusing),
            list(label = 'Jaw-dropping', values = ~'Jaw-dropping'),
            list(label = 'Longwinded', values = ~Longwinded)
            )
          )

```

