---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=F, warning=F)
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(RColorBrewer)
library(plotly) #contain hex to RGB conversion
#forbes
library(forbesListR)
#date
library(lubridate)
#machinelearning
library(caret)

#text
library(tidytext)

#theme
my_theme <- function(base_size = 12, base_family = "Helvetica"){
    theme_minimal() +
    theme(axis.title.y = element_blank(),axis.title.x = element_blank(),
    plot.title = element_text(face="bold", size=16),
    axis.text = element_text(face="bold"),
    plot.background = element_rect(fill = 'ghostwhite',color='white'),
    legend.position = 'None', legend.title = element_blank())
}

```

## Load data
Question we seek to answer:

* demography of midas listers: gender, location, age
* how does midas lister in the past 6 years: newcomers and leavers
* which notable companies were invested by multiple midas lister?
* network of notable companies with VC firm affliated with midas lister?
* people invested in company x also invested in company y


```{r input}
#this forbes pkg conflicts with igraph package due to as_data_frame(), load igraph later
#2012/2013 has 50-60 with missing ages whereas 2015/16 has only 1 missing
df <- get_years_forbes_list_data(years = 2013:2017, list_name = "Top VCs")
#alternative df <- read_csv("~/git_repo/opendata_viz/midas_list/midas_2012_2017.csv") %>% filter(year>2012)
```

## cleaning data
```{r}
df <- df %>% mutate(name=ifelse(name=='Mike Maples','Mike Maples, Jr.',name))
```

There are 87 company, 172 investor and 163 notable investments listed

## notable investor and deals

```{r}
df%>%
  group_by(name) %>%
  summarize(n_company = n_distinct(notableDeal)) %>%
  arrange(desc(n_company))
```

```{r}
df %>%
  group_by(notableDeal) %>%
  summarize(n_lister = n_distinct(name)) %>%
  arrange(desc(n_lister))
```


#1. demographics
```{r}
library(waffle)
df%>%filter(year==2017)%$%table(gender)

parts <- c(Female=6, Male=94)

waffle(parts, rows=10, colors=c("pink", "#969696"), 
       title="Midas List 2017", legend_pos="bottom")
```
```{r}
x= df%>%
  filter(year==2017)%$%table(country)

waffle(x, rows=10, 
       colors=c("tan", "darkcyan","blueviolet","grey50",
                "lightseagreen","brown","slateblue4","beige","lightblue"), 
       title="Midas List 2017", legend_pos="bottom")
```


#2. compare the lister

```{r}
yrs <-split(df,df$year)
yr2013=yrs[[1]]
yr2014=yrs[[2]]
yr2015=yrs[[3]]
yr2016=yrs[[4]]
yr2017=yrs[[5]]
```


```{r}
status_change = function(df1,df2,df3) {
  df2 %>%
    mutate(type = 
             ifelse(name %in% setdiff(df2$name,df3$name), "left",
                           ifelse(name %in% setdiff(df2$name,df1$name), "new",
                                    'same'))) 
}
```



```{r}
df17= yr2017 %>% mutate(type= ifelse(name %in% setdiff(yr2017$name,yr2016$name), "new",
                                    'same'))
```

```{r}
#testing
# s=df2 %>%
#     mutate(type = ifelse(name %in% setdiff(df2$name,df1$name), "new",
#                                     'same'))
```


```{r}
df_change <- status_change(NULL, yr2013, yr2014) %>%
  rbind(status_change(yr2013, yr2014, yr2015))%>%
  rbind(status_change(yr2014, yr2015, yr2016))%>%
  rbind(status_change(yr2015, yr2016, yr2017))%>%
  rbind(df17)
```

```{r}
#handle first/last year no-comparables
df_change <- df_change %>%
  mutate(type=ifelse(year==2013,gsub("new","same",type),
                      ifelse(year==2017,gsub("left","same",type),type)))
```

```{r}
df_change_rank <- df_change %>%
  select(year, rank, name, type, company, notableDeal, url.image, gender, country) %>%
  mutate(rank_bkt=cut_interval(rank, length=25))
```


```{r}
write.csv(df_change_rank, 'df_change_rank.csv')
```

# network

```{r}
g <- df %>% na.omit() %>% graph_from_data_frame()

V(g)$Popularity <- degree(g)

g %>%
  ggraph(layout = "fr") +
  geom_edge_link(show.legend = FALSE) +
  geom_node_point(color = "purple") +
  geom_node_text( aes(label = ifelse(Popularity>=4, V(g)$name,'')), size=3, repel = TRUE) +
  theme_void() + 
  theme(legend.position = 'None')
```


# companies invested by same midas listers

```{r}
co_occur = sqldf("SELECT a.occupation2 a, b.occupation2 b, COUNT(*) cnt
FROM  occupation a 
JOIN occupation b 
ON b.name = a.name AND b.occupation2 > a.occupation2
GROUP BY a.occupation2, b.occupation2")

g <- co_occur %>% 
  graph_from_data_frame() 

V(g)$Popularity <- degree(g)
length(V(g)$name)
E(g)$year <- as.character(E(g)$year)
```
## Speakers wearing multiple hats

```{r ggraph}

g %>%
  ggraph(layout = 'fr') +
  geom_edge_link(aes(edge_alpha = cnt),edge_colour = 'white',  show.legend = FALSE) +
  geom_edge_density(aes(fill = 'white')) + 
  geom_node_point(color = "white",aes(size = Popularity)) +
  geom_node_text(color = "ghostwhite", aes(label = ifelse(Popularity>=10, V(g)$name,'')), size=3, repel = TRUE) +
  theme_void() + 
  theme(legend.position = 'None',
        plot.background = element_rect(fill = '#300961',color='grey'),
        plot.margin=unit(c(1.2,1.2,1.2,1.2),"cm")) + coord_equal()

```


```{r}
g <- df %>% na.omit() %>% graph_from_data_frame()

V(g)$Popularity <- degree(g)

g %>%
  ggraph(layout = "fr") +
  geom_edge_link(show.legend = FALSE) +
  geom_node_point(color = "purple") +
  geom_node_text( aes(label = ifelse(Popularity>=4, V(g)$name,'')), size=3, repel = TRUE) +
  theme_void() + 
  theme(legend.position = 'None')
```

## Takeaways